---
title: "Baseline analysis supplement"
---

```{r setup}
library(papaja)
library(knitr)
library(tidyverse)
opts_chunk$set(echo = TRUE, 
               warning = TRUE,
               error = TRUE,
               cache = TRUE, 
               collapse = TRUE,
               eval = TRUE)
opts_chunk$set(root.dir = ".")  # Always project root as working directory
opts_knit$set(root.dir = ".")  # This is needed for some versions of RStudio
```

```{r set-viz-theme}
theme_set(theme_apa())
```

# Load packages and data

```{r}
#.libPaths("C:/R/R-3.4.2/library")
#.libPaths("C:/Users/hema/RPackages")
#.libPaths("C:/rlibs/3.4.2")

if (!require(pacman)) install.packages("pacman")
library(pacman)

p_load(tidyverse, haven, lme4, userfriendlyscience, grid, sm, sjstats, gridExtra, ggridges, igraph, devtools)

lmi <- read_sav("data/LMI_data_korjattu_syntaksilla.sav", user_na = FALSE)
# write_csv(lmi, "Z:/Desktop/LMI DATA/LMI_data_korjattu_syntaksilla_CSV.csv")

# to get rid of DLL warning, these don't work: 
# Sys.setenv("R_MAX_NUM_DLLS" = 1000)
# remove.packages(c("rethinking"))
# detach("package:rethinking", unload=TRUE)

# Unloading all packages gives LAPACK error:
# pkgs <- names(sessionInfo()$otherPkgs)
# pkgs <- paste('package:', pkgs, sep = "")
# lapply(pkgs, detach, character.only = TRUE, unload = TRUE)
```

## Package sm modifications

**Code to set up the modified function**

```{r sm, verbose = FALSE}

# Changing the sm density compare function to allow different color of the band of equality. Copied from https://web.archive.org/web/20170222214214/https://stat.ethz.ch/pipermail/r-help//2009-March/416920.html.

sm.density.compare2 <- function (x, group, h, model = "none", bandcol =
                                  'cyan', lwd = par("lwd"), usePolyg = NULL, asp=NA, 
                                xlab=opt$xlab, ylab=opt$ylab, ...) 
{
  if (!is.vector(x)) 
    stop("sm.density.compare can handle only 1-d data")
  opt <- sm.options(list(...))
  sm:::replace.na(opt, ngrid, 50)                 
  ## These all changed from replace.na() --> sm:::
  sm:::replace.na(opt, display, "line")
  sm:::replace.na(opt, xlab, deparse(substitute(x)))
  sm:::replace.na(opt, ylab, "Density")
  sm:::replace.na(opt, xlim, c(min(x) - diff(range(x))/4, max(x) + 
                                 diff(range(x))/4))
  sm:::replace.na(opt, eval.points, seq(opt$xlim[1], opt$xlim[2], 
                                        length = opt$ngrid))
  if (is.na(opt$band)) {
    if (model == "none") 
      opt$band <- FALSE
    else opt$band <- TRUE
  }
  if ((model == "none") && opt$band) 
    opt$band <- FALSE
  band <- opt$band
  ngrid <- opt$ngrid
  xlim <- opt$xlim
  nboot <- opt$nboot
  y <- x
  if (is.na(opt$test)) {
    if (model == "none") 
      opt$test <- FALSE
    else opt$test <- TRUE
  }
  if ((model == "none") && opt$test) 
    opt$test <- FALSE
  test <- opt$test
  if (opt$display %in% "none") 
    band <- FALSE
  fact <- factor(group)
  fact.levels <- levels(fact)
  nlev <- length(fact.levels)
  ni <- table(fact)
  if (band & (nlev > 2)) {
    cat("Reference band available to compare two groups only.", 
        "\n")
    band <- FALSE
  }
  if (length(opt$lty) < nlev) 
    opt$lty <- 1:nlev
  if (length(opt$col) < nlev) 
    opt$col <- 2:(nlev + 1)
  if (missing(h)) 
    h <- h.select(x, y = NA, group = group, ...)
  opt$band <- band
  opt$test <- test
  estimate <- matrix(0, ncol = opt$ngrid, nrow = nlev)
  se <- matrix(0, ncol = opt$ngrid, nrow = nlev)
  for (i in 1:nlev) {
    sm <- sm.density(y[fact == fact.levels[i]], h = h, display = "none", 
                     eval.points = opt$eval.points)
    estimate[i, ] <- sm$estimate
    se[i, ] <- sm$se
  }
  eval.points <- sm$eval.points
  if (!(opt$display %in% "none" | band)) {
    plot(xlim, c(0, 1.1 * max(as.vector(estimate))), xlab = opt$xlab, 
         ylab = opt$ylab, type = "n")
    #for (i in 1:nlev) lines(eval.points, estimate[i, ], lty = opt$lty[i], 
    #    col = opt$col[i])
    for (i in 1:nlev) lines(eval.points, estimate[i, ], lty =
                              opt$lty[i],   ## lwd hacked in
                            col = opt$col[i], lwd = lwd[i])
  }
  est <- NULL
  p <- NULL
  if (model == "equal" & test) {
    if (nlev == 2) {
      ts <- sum((estimate[1, ] - estimate[2, ])^2)
    }
    else {
      sm.mean <- sm.density(y, h = h, xlim = opt$xlim, 
                            ngrid = opt$ngrid, display = "none")$estimate
      ts <- 0
      for (i in 1:nlev) ts <- ts + ni[i] * sum((estimate[i, 
                                                         ] - sm.mean)^2)
    }
    p <- 0
    est.star <- matrix(0, ncol = opt$ngrid, nrow = nlev)
    for (iboot in 1:nboot) {
      ind <- (1:length(y))
      for (i in 1:nlev) {
        indi <- sample((1:length(ind)), ni[i])
        est.star[i, ] <- sm.density(y[ind[indi]], h = h, 
                                    ngrid = opt$ngrid, xlim = opt$xlim, display =
                                      "none")$estimate
        ind <- ind[-indi]
      }
      if (nlev == 2) {
        ts.star <- sum((est.star[1, ] - est.star[2, ])^2)
      }
      else {
        sm.mean <- sm.density(y, h = h, xlim = opt$xlim, 
                              ngrid = opt$ngrid, display = "none")$estimate
        ts.star <- 0
        for (i in 1:nlev) {
          ts.star <- ts.star + ni[i] * sum((est.star[i, 
                                                     ] - sm.mean)^2)
        }
      }
      if (ts.star > ts) 
        p <- p + 1
      if (opt$verbose > 1) {
        cat(iboot)
        cat(" ")
      }
    }
    p <- p/nboot
    cat("\nTest of equal densities:  p-value = ", round(p, 
                                                        5), "\n")
    est <- list(p = p, h = h)
  }
  if (model == "equal" & band) {
    av <- (sqrt(estimate[1, ]) + sqrt(estimate[2, ]))/2
    se <- sqrt(se[1, ]^2 + se[2, ]^2)
    upper <- (av + se)^2
    lower <- pmax(av - se, 0)^2
    plot(xlim, c(0, 1.1 * max(as.vector(estimate), upper)), 
         xlab = xlab, ylab = ylab, type = "n", asp=asp, ...)     
    ## ... and asp added; was opt$xlab and opt$ylab
    polygon(c(eval.points, rev(eval.points)), c(upper, rev(lower)), 
            col = bandcol, border = 0)                                      
    ## was col = "cyan"
    if (is.null(usePolyg)) {
      lines(eval.points, estimate[1, ], lty = opt$lty[1], col =
              opt$col[1], lwd = lwd[1])
      lines(eval.points, estimate[2, ], lty = opt$lty[2], col =
              opt$col[2], lwd = lwd[2])
    }
    else {
      polygon(eval.points, estimate[1, ], lty = opt$lty[1], col =
                opt$col[1], lwd = lwd[1])
      polygon(eval.points, estimate[2, ], lty = opt$lty[2], col =
                opt$col[2], lwd = lwd[2])
    }
    est <- list(p = p, upper = upper, lower = lower, h = h)
  }
  invisible(est)
}

```

# Prepare data with variables of interest

```{r}
library(userfriendlyscience)

d <- lmi %>% dplyr::select(id = ID,
  intervention = ryhmä,
  group = ryhmäkoodi_korjattu,
  school = Aineisto.1,
  girl = Kys0013.1,
b5agr_01_T1 = Kys0155.1,
b5agrNeg_02_T1 = Kys0150.1,
b5cons_01_T1 = Kys0151.1,
b5consNeg_02_T1 = Kys0156.1,
b5ext_01_T1 = Kys0149.1,
b5extNeg_02_T1 = Kys0154.1,
b5neur_01_T1 = Kys0152.1,
b5neurNeg_02_T1 = Kys0157.1,
b5open_01_T1 = Kys0153.1,
b5openNeg_02_T1 = Kys0158.1,
fatpct_T1 = Rasva,
PA_actCop_01_T1 = Kys0115.1,
PA_actCop_01_T3 = Kys0115.3,
PA_actCop_02_T1 = Kys0116.1,
PA_actCop_02_T3 = Kys0116.3,
PA_actCop_03_T1 = Kys0117.1,
PA_actCop_03_T3 = Kys0117.3,
PA_actCop_04_T1 = Kys0118.1,
PA_actCop_04_T3 = Kys0118.3,
PA_agrbct_01_T1 = Kys0128.1,
PA_agrbct_01_T3 = Kys0128.3,
PA_agrbct_02_T1 = Kys0129.1,
PA_agrbct_02_T3 = Kys0129.3,
PA_agrbct_03_T1 = Kys0130.1,
PA_agrbct_03_T3 = Kys0130.3,
PA_agrbct_04_T1 = Kys0131.1,
PA_agrbct_04_T3 = Kys0131.3,
PA_agrbct_05_T1 = Kys0132.1,
PA_agrbct_05_T3 = Kys0132.3,
PA_agrbct_06_T1 = Kys0133.1,
PA_agrbct_06_T3 = Kys0133.3,
PA_agrbct_07_T1 = Kys0134.1,
PA_agrbct_07_T3 = Kys0134.3,
PA_agrbct_08_T1 = Kys0135.1,
PA_agrbct_08_T3 = Kys0135.3,
PA_agrbct_09_T1 = Kys0136.1,
PA_agrbct_09_T3 = Kys0136.3,
PA_agrbct_10_T1 = Kys0137.1,
PA_agrbct_10_T3 = Kys0137.3,
PA_amotivation_01_T1 = Kys0082.1,
PA_amotivation_01_T3 = Kys0082.3,
PA_amotivation_02_T1 = Kys0086.1,
PA_amotivation_02_T3 = Kys0086.3,
PA_amotivation_03_T1 = Kys0096.1,
PA_amotivation_03_T3 = Kys0096.3,
PA_amotivation_04_T1 = Kys0097.1,
PA_amotivation_04_T3 = Kys0097.3,
PA_actCop_05_T1 = Kys0119.1,
PA_actCop_05_T3 = Kys0119.3,
PA_actCop_06_T1 = Kys0120.1,
PA_actCop_06_T3 = Kys0120.3,
PA_actCop_07_T1 = Kys0121.1,
PA_actCop_07_T3 = Kys0121.3,
PA_actCop_08_T1 = Kys0122.1,
PA_actCop_08_T3 = Kys0122.3,
PA_dnorm_02_T1 = Kys0107.1,
PA_dnormparents_02_T3 = Kys0107.3,
PA_dnorm_01_T1 = Kys0106.1,
PA_dnorm_01_T3 = Kys0106.3,
PA_controlled_01_T1 = Kys0080.1,
PA_controlled_01_T3 = Kys0080.3,
PA_controlled_02_T1 = Kys0081.1,
PA_controlled_02_T3 = Kys0081.3,
PA_controlled_03_T1 = Kys0083.1,
PA_controlled_03_T3 = Kys0083.3,
PA_frqbct_01_T1 = Kys0138.1,
PA_frqbct_01_T3 = Kys0138.3,
PA_frqbct_02_T1 = Kys0139.1,
PA_frqbct_02_T3 = Kys0139.3,
PA_frqbct_03_T1 = Kys0140.1,
PA_frqbct_03_T3 = Kys0140.3,
PA_frqbct_04_T1 = Kys0141.1,
PA_frqbct_04_T3 = Kys0141.3,
PA_frqbct_05_T1 = Kys0142.1,
PA_frqbct_05_T3 = Kys0142.3,
PA_frqbct_06_T1 = Kys0143.1,
PA_frqbct_06_T3 = Kys0143.3,
PA_frqbct_07_T1 = Kys0144.1,
PA_frqbct_07_T3 = Kys0144.3,
PA_frqbct_08_T1 = Kys0145.1,
PA_frqbct_08_T3 = Kys0145.3,
PA_frqbct_09_T1 = Kys0146.1,
PA_frqbct_09_T3 = Kys0146.3,
PA_goal_01_T1 = Kys0147.1,
PA_goal_01_T3 = Kys0147.3,
PA_autonomous_01_T1 = Kys0087.1,
PA_autonomous_01_T3 = Kys0087.3,
PA_autonomous_02_T1 = Kys0088.1,
PA_autonomous_02_T3 = Kys0088.3,
PA_autonomous_03_T1 = Kys0090.1,
PA_autonomous_03_T3 = Kys0090.3,
PA_inorm_01_T1 = Kys0108.1,
PA_inorm_01_T3 = Kys0108.3,
PA_autonomous_04_T1 = Kys0089.1,
PA_autonomous_04_T3 = Kys0089.3,
PA_autonomous_05_T1 = Kys0092.1,
PA_autonomous_05_T3 = Kys0092.3,
PA_autonomous_06_T1 = Kys0094.1,
PA_autonomous_06_T3 = Kys0094.3,
PA_intention_01_T1 = Kys0113.1,
PA_intention_01_T3 = Kys0113.3,
PA_intention_02_T1 = Kys0114.1,
PA_intention_02_T3 = Kys0114.3,
PA_autonomous_07_T1 = Kys0091.1,
PA_autonomous_07_T3 = Kys0091.3,
PA_autonomous_08_T1 = Kys0093.1,
PA_autonomous_08_T3 = Kys0093.3,
PA_autonomous_09_T1 = Kys0095.1,
PA_autonomous_09_T3 = Kys0095.3,
PA_controlled_04_T1 = Kys0084.1,
PA_controlled_04_T3 = Kys0084.3,
PA_controlled_05_T1 = Kys0085.1,
PA_controlled_05_T3 = Kys0085.3,
PA_oexp_01_T1 = Kys0068.1,
PA_oexp_01_T3 = Kys0068.3,
PA_oexp_03_T1 = Kys0070.1,
PA_oexp_03_T3 = Kys0070.3,
PA_oexp_04_T1 = Kys0071.1,
PA_oexp_04_T3 = Kys0071.3,
PA_oexp_05_T1 = Kys0072.1,
PA_oexp_05_T3 = Kys0072.3,
PA_oexp_06_T1 = Kys0073.1,
PA_oexp_06_T3 = Kys0073.3,
PA_oexp_07_T1 = Kys0074.1,
PA_oexp_07_T3 = Kys0074.3,
PA_oexp_10_T1 = Kys0077.1,
PA_oexp_10_T3 = Kys0077.3,
PA_oexp_11_T1 = Kys0078.1,
PA_oexp_11_T3 = Kys0078.3,
PA_oexp_12_T1 = Kys0079.1,
PA_oexp_12_T3 = Kys0079.3,
PA_oexpNeg_02_T1 = Kys0069.1,
PA_oexpNeg_02_T3 = Kys0069.3,
PA_oexpNeg_08_T1 = Kys0075.1,
PA_oexpNeg_08_T3 = Kys0075.3,
PA_oexpNeg_09_T1 = Kys0076.1,
PA_oexpNeg_09_T3 = Kys0076.3,
PA_opportunities_01_T1 = Kys0098.1,
PA_opportunities_01_T3 = Kys0098.3,
PA_opportunities_02_T1 = Kys0099.1,
PA_opportunities_02_T3 = Kys0099.3,
PA_opportunities_04_T1 = Kys0101.1,
PA_opportunities_04_T3 = Kys0101.3,
PA_opportunities_05_T1 = Kys0102.1,
PA_opportunities_05_T3 = Kys0102.3,
PA_opportunities_07_T1 = Kys0104.1,
PA_opportunities_07_T3 = Kys0104.3,
PA_opportunitiesNeg_03_T1 = Kys0100.1,
PA_opportunitiesNeg_03_T3 = Kys0100.3,
PA_opportunitiesNeg_06_T1 = Kys0103.1,
PA_opportunitiesNeg_06_T3 = Kys0103.3,
PA_opportunitiesNeg_08_T1 = Kys0105.1,
# No answers or not asked T3: PA_opportunitiesNeg_08_T3 = Kys0105.3,
PA_pbc_01_T1 = Kys0125.1,
PA_pbc_01_T3 = Kys0125.3,
PA_pbc_03_T1 = Kys0127.1,
PA_pbc_03_T3 = Kys0127.3,
PA_pbcNeg_02_T1 = Kys0126.1,
PA_pbcNeg_02_T3 = Kys0126.3,
PA_selfefficacy_01_T1 = Kys0123.1,
PA_selfefficacy_01_T3 = Kys0123.3,
PA_selfefficacyNeg_02_T1 = Kys0124.1,
PA_selfefficacyNeg_02_T3 = Kys0124.3,
paAccelerometer_T1 = LiikuntaT1_ka,
paAccelerometer_T3 = LiikuntaT3_ka,
padaysLastweek_T1 = Kys0045.1,
padaysLastweek_T3 = Kys0045.3,
pafreqUsually_T1 = Kys0048.1,
pafreqUsually_T3 = Kys0048.3,
pahrsLastweek_T1 = Kys0046.1,
pahrsLastweek_T3 = Kys0046.3,
pahrsUsually_T1 = Kys0049.1,
pahrsUsually_T3 = Kys0049.3,
paminLastweek_T1 = Kys0047.1,
paminLastweek_T3 = Kys0047.3,
SB_dnorm_01_T1 = Kys0178.1,
SB_dnorm_01_T3 = Kys0178.3,
SB_dnorm_02_T1 = Kys0179.1,
SB_dnorm_02_T3 = Kys0179.3,
SB_inorm_01_T1 = Kys0180.1,
SB_inorm_01_T3 = Kys0180.3,
SB_inorm_02_T1 = Kys0181.1,
SB_inorm_02_T3 = Kys0181.3,
SB_intention_01_T1 = Kys0187.1,
SB_intention_01_T3 = Kys0187.3,
SB_intention_02_T1 = Kys0188.1,
SB_intention_02_T3 = Kys0188.3,
SB_intention_03_T1 = Kys0189.1,
SB_intention_03_T3 = Kys0189.3,
SB_intention_04_T1 = Kys0190.1,
SB_intention_04_T3 = Kys0190.3,
SB_oexpNeg_01_T1 = Kys0171.1,
SB_oexpNeg_01_T3 = Kys0171.3,
SB_oexp_02_T1 = Kys0172.1,
SB_oexp_02_T3 = Kys0172.3,
SB_oexp_03_T1 = Kys0173.1,
SB_oexp_03_T3 = Kys0173.3,
SB_oexp_04_T1 = Kys0174.1,
SB_oexp_04_T3 = Kys0174.3,
SB_oexp_05_T1 = Kys0175.1,
SB_oexp_05_T3 = Kys0175.3,
SB_oexp_06_T1 = Kys0176.1,
SB_oexp_06_T3 = Kys0176.3,
SB_oexpNeg_07_T1 = Kys0177.1,
SB_oexpNeg_07_T3 = Kys0177.3,
SB_sePbc_01_T1 = Kys0182.1,
SB_sePbc_01_T3 = Kys0182.3,
SB_sePbc_02_T1 = Kys0183.1,
SB_sePbc_02_T3 = Kys0183.3,
SB_sePbc_03_T1 = Kys0184.1,
SB_sePbc_03_T3 = Kys0184.3,
SB_sePbc_04_T1 = Kys0185.1,
SB_sePbc_04_T3 = Kys0185.3,
SB_sePbc_05_T1 = Kys0186.1,
SB_sePbc_05_T3 = Kys0186.3,
sitLieAccelerometer_T1 = MaIsT1_ka,
sitLieAccelerometer_T3 = MaIsT3_ka,
symptom_neckShoulderPain_T1 = Kys0031.1,
symptom_neckShoulderPain_T3 = Kys0031.3,
symptom_lowerBackPain_T1 = Kys0032.1,
symptom_lowerBackPain_T3 = Kys0032.3,
symptom_stomachAche_T1 = Kys0033.1,
symptom_stomachAche_T3 = Kys0033.3,
symptom_tensionNervousness_T1 = Kys0034.1,
symptom_tensionNervousness_T3 = Kys0034.3,
symptom_irritabilityAngerbursts_T1 = Kys0035.1,
symptom_irritabilityAngerbursts_T3 = Kys0035.3,
symptom_sleepDifficulty_T1 = Kys0036.1,
symptom_sleepDifficulty_T3 = Kys0036.3,
symptom_headAche_T1 = Kys0037.1,
symptom_headAche_T3 = Kys0037.3,
symptom_tirednessFaintness_T1 = Kys0038.1,
symptom_tirednessFaintness_T3 = Kys0038.3,
PA_actplan_01_T1 = Kys0115.1,
PA_actplan_02_T1 = Kys0116.1,
PA_actplan_03_T1 = Kys0117.1,
PA_actplan_04_T1 = Kys0118.1,
PA_copplan_01_T1 = Kys0119.1,
PA_copplan_02_T1 = Kys0120.1,
PA_copplan_03_T1 = Kys0121.1,
PA_copplan_04_T1 = Kys0122.1,
PA_actplan_01_T3 = Kys0115.3,
PA_actplan_02_T3 = Kys0116.3,
PA_actplan_03_T3 = Kys0117.3,
PA_actplan_04_T3 = Kys0118.3,
PA_copplan_01_T3 = Kys0119.3,
PA_copplan_02_T3 = Kys0120.3,
PA_copplan_03_T3 = Kys0121.3,
PA_copplan_04_T3 = Kys0122.3,
sitBreaks_T1 = YlösT1_ka
)

# Reverse coded items to normal: 
# Take vars that contain "Neg_", substract them from 8 (each scale is 1-7)
d <- d %>% mutate_at(dplyr::vars(contains("Neg_")), funs(8 - .))

# To check:
# d %>% select(contains("Neg_")), contains("Rev")) %>% View
identical(as.numeric(8 - lmi$Kys0154.1), as.numeric(d$b5extNeg_02_T1))
identical(as.numeric(8 - lmi$Kys0100.1), as.numeric(d$PA_opportunitiesNeg_03_T1))

# Group variable has empty missings
d <- d %>% dplyr::mutate(group = ifelse(group == "", NA, group))

# Fix intervention and gender variables
d <- d %>% dplyr::mutate(intervention = ifelse(intervention == 1, 1, 0),
                         intervention = factor(intervention),
            girl = ifelse(girl == 2, 1, 0),
            girl = factor(girl, levels = c("1", "0")),
            school = factor(school, levels = c("1", "2", "3", "4", "5")))

# Create the self-reported PA time variable
d <- d %>% dplyr::mutate(paLastweek_T1 = (pahrsLastweek_T1 * 60) + ifelse(paminLastweek_T1 == 2, 30, 0))

# Insert track variable with those who answered "other" with one of the actual category labels given the appropriate category:
track <- lmi %>% select(Kys0016.1, Kys0017.1) %>% mutate(
  Kys0016.1 = ifelse(Kys0017.1 == "Merkonomi" | Kys0017.1 == "merkonomi", 3,
                  ifelse(Kys0017.1 == "Datanomi" | Kys0017.1 == "datanomi", 2, Kys0016.1)),
  track = factor(Kys0016.1, # Fix track labels first
                     levels = c(0, 1, 2, 3, 4),
                     labels = c("Other", "Business IT", "Business Admin", "HRC", "Nursing"))) %>% 
  select(-Kys0016.1, -Kys0017.1)

d <- bind_cols(d, track)

dT1 <- d %>% select(contains("T1"))
dT3 <- d %>% select(contains("T3"))

# Create T1 scales

scales_T1 <- list(b5agr_T1 = grep('b5agr', names(dT1), value = TRUE),
b5cons_T1 = grep('b5cons', names(dT1), value = TRUE),
b5ext_T1 = grep('b5ext', names(dT1), value = TRUE),
b5neur_T1 = grep('b5neur', names(dT1), value = TRUE),
b5open_T1 = grep('b5open', names(dT1), value = TRUE),
PA_actCop_T1 = grep('PA_actCop', names(dT1), value = TRUE),
PA_agrbct_T1 = grep('PA_agrbct', names(dT1), value = TRUE),
PA_amotivation_T1 = grep('PA_amotivation', names(dT1), value = TRUE),
PA_autonomous_T1 = grep('PA_autonomous', names(dT1), value = TRUE),
PA_controlled_T1 = grep('PA_controlled', names(dT1), value = TRUE),
PA_dnorm_T1 = grep('PA_dnorm', names(dT1), value = TRUE),
PA_frqbct_T1 = grep('PA_frqbct', names(dT1), value = TRUE),
PA_goal_T1 = grep('PA_goal', names(dT1), value = TRUE),
PA_inorm_T1 = grep('PA_inorm', names(dT1), value = TRUE),
PA_intention_T1 = grep('PA_intention', names(dT1), value = TRUE),
PA_oexp_T1 = grep('PA_oexp', names(dT1), value = TRUE),
PA_opportunities_T1 = grep('PA_opportunities', names(dT1), value = TRUE),
PA_pbc_T1 = grep('PA_pbc', names(dT1), value = TRUE),
PA_selfefficacy_T1 = grep('PA_selfefficacy', names(dT1), value = TRUE),
SB_dnorm_T1 = grep('SB_dnorm', names(dT1), value = TRUE),
SB_inorm_T1 = grep('SB_inorm', names(dT1), value = TRUE),
SB_intention_T1 = grep('SB_intention', names(dT1), value = TRUE),
SB_oexp_T1 = grep('SB_oexp', names(dT1), value = TRUE),
SB_sePbc_T1 = grep('SB_sePbc', names(dT1), value = TRUE),
symptom_T1 = grep('symptom', names(dT1), value = TRUE),
PA_actionplan_T1 = grep('actplan', names(dT1), value = TRUE),
PA_copingplan_T1 = grep('copplan', names(dT1), value = TRUE)
)

# Append the aggregate variables to the data frame
newdf <- makeScales(dT1, scales_T1)

# Create T3 scales

scales_T3 <- list(b5agr_T3 = grep('b5agr', names(dT3), value = TRUE),
b5cons_T3 = grep('b5cons', names(dT3), value = TRUE),
b5ext_T3 = grep('b5ext', names(dT3), value = TRUE),
b5neur_T3 = grep('b5neur', names(dT3), value = TRUE),
b5open_T3 = grep('b5open', names(dT3), value = TRUE),
PA_actCop_T3 = grep('PA_actCop', names(dT3), value = TRUE),
PA_agrbct_T3 = grep('PA_agrbct', names(dT3), value = TRUE),
PA_amotivation_T3 = grep('PA_amotivation', names(dT3), value = TRUE),
PA_autonomous_T3 = grep('PA_autonomous', names(dT3), value = TRUE),
PA_controlled_T3 = grep('PA_controlled', names(dT3), value = TRUE),
PA_dnorm_T3 = grep('PA_dnorm', names(dT3), value = TRUE),
PA_frqbct_T3 = grep('PA_frqbct', names(dT3), value = TRUE),
PA_goal_T3 = grep('PA_goal', names(dT3), value = TRUE),
PA_inorm_T3 = grep('PA_inorm', names(dT3), value = TRUE),
PA_intention_T3 = grep('PA_intention', names(dT3), value = TRUE),
PA_oexp_T3 = grep('PA_oexp', names(dT3), value = TRUE),
PA_opportunities_T3 = grep('PA_opportunities', names(dT3), value = TRUE),
PA_pbc_T3 = grep('PA_pbc', names(dT3), value = TRUE),
PA_selfefficacy_T3 = grep('PA_selfefficacy', names(dT3), value = TRUE),
SB_dnorm_T3 = grep('SB_dnorm', names(dT3), value = TRUE),
SB_inorm_T3 = grep('SB_inorm', names(dT3), value = TRUE),
SB_intention_T3 = grep('SB_intention', names(dT3), value = TRUE),
SB_oexp_T3 = grep('SB_oexp', names(dT3), value = TRUE),
SB_sePbc_T3 = grep('SB_sePbc', names(dT3), value = TRUE),
symptom_T3 = grep('symptom', names(dT3), value = TRUE),
PA_actionplan_T3 = grep('actplan', names(dT3), value = TRUE),
PA_copingplan_T3 = grep('copplan', names(dT3), value = TRUE)
)

# Append the aggregate variables to the data frame
newdf2 <- makeScales(dT3, scales_T3)

# Take the demographic variables from d, combine with the variables with T1 or T3 in the name. 
df <- cbind(d[ , c("id", "intervention", "group", "school", "girl", "track")], newdf[, ], newdf2[, ])

# Create composite of self-efficacy and perceived behavioural control
df <- df %>% rowwise %>%
    mutate(PA_sePbc_T1 = mean(c(PA_pbc_T1, PA_selfefficacy_T1), na.rm = T),
           PA_sePbc_T3 = mean(c(PA_pbc_T3, PA_selfefficacy_T3), na.rm = T))
## Fix the "NaN"s
df$PA_sePbc_T1[is.nan(df$PA_sePbc_T1)] <- NA
df$PA_sePbc_T3[is.nan(df$PA_sePbc_T3)] <- NA

# Create composite of action planning and coping planning
df <- df %>% rowwise %>%
    mutate(PA_actCop_T1 = mean(c(PA_actionplan_T1, PA_copingplan_T1), na.rm = T),
           PA_actCop_T3 = mean(c(PA_actionplan_T3, PA_copingplan_T3), na.rm = T))
## Fix the "NaN"s
df$PA_actCop_T1[is.nan(df$PA_actCop_T1)] <- NA
df$PA_actCop_T3[is.nan(df$PA_actCop_T3)] <- NA

# Create variables for motivational regulations

regulationVariables_T1 <- lmi %>% select(
  PA_extrinsic_01_T1 = Kys0080.1,
  PA_extrinsic_02_T1 = Kys0081.1,
  PA_extrinsic_03_T1 = Kys0083.1,
  PA_introjected_01_T1 = Kys0084.1,
  PA_introjected_02_T1 = Kys0085.1,
  PA_identified_01_T1 = Kys0087.1,
  PA_identified_02_T1 = Kys0088.1,
  PA_identified_03_T1 = Kys0090.1,
  PA_integrated_01_T1 = Kys0089.1,
  PA_integrated_02_T1 = Kys0092.1,
  PA_integrated_03_T1 = Kys0094.1,
  PA_intrinsic_01_T1 = Kys0091.1,
  PA_intrinsic_02_T1 = Kys0093.1,
  PA_intrinsic_03_T1 = Kys0095.1)

regulationVariables_T3 <- lmi %>% select(
  PA_extrinsic_01_T3 = Kys0080.3,
  PA_extrinsic_02_T3 = Kys0081.3,
  PA_extrinsic_03_T3 = Kys0083.3,
  PA_introjected_01_T3 = Kys0084.3,
  PA_introjected_02_T3 = Kys0085.3,
  PA_identified_01_T3 = Kys0087.3,
  PA_identified_02_T3 = Kys0088.3,
  PA_identified_03_T3 = Kys0090.3,
  PA_integrated_01_T3 = Kys0089.3,
  PA_integrated_02_T3 = Kys0092.3,
  PA_integrated_03_T3 = Kys0094.3,
  PA_intrinsic_01_T3 = Kys0091.3,
  PA_intrinsic_02_T3 = Kys0093.3,
  PA_intrinsic_03_T3 = Kys0095.3
)

motiscales_T1 <- list(
  PA_intrinsic_T1 = grep('intrinsic', names(regulationVariables_T1), value = TRUE),
  PA_integrated_T1 = grep('integrated', names(regulationVariables_T1), value = TRUE),
  PA_identified_T1 = grep('identified', names(regulationVariables_T1), value = TRUE),
  PA_introjected_T1 = grep('introjected', names(regulationVariables_T1), value = TRUE),
  PA_extrinsic_T1 = grep('extrinsic', names(regulationVariables_T1), value = TRUE))

motiscales_T3 <- list(
  PA_intrinsic_T3 = grep('intrinsic', names(regulationVariables_T3), value = TRUE),
  PA_integrated_T3 = grep('integrated', names(regulationVariables_T3), value = TRUE),
  PA_identified_T3 = grep('identified', names(regulationVariables_T3), value = TRUE),
  PA_introjected_T3 = grep('introjected', names(regulationVariables_T3), value = TRUE),
  PA_extrinsic_T3 = grep('extrinsic', names(regulationVariables_T3), value = TRUE))

motidf1 <- makeScales(regulationVariables_T1, motiscales_T1)
motidf2 <- makeScales(regulationVariables_T3, motiscales_T3)

df <- cbind(df, motidf1, motidf2)

# Create change scores
t1_vars <- grep("_T1", colnames(df), value = TRUE)
t1_vars <- grep("b5|fat|paLastweek|PA_opportunitiesNeg_08|sitBreaks_T1", t1_vars, value = TRUE, invert = TRUE) # drop variables not in T3
t3_vars <- grep("_T3", colnames(df), value = TRUE)
df[, paste0(str_sub(t1_vars, end = -4), "_diff")] <- df[, t3_vars] - df[, t1_vars]


```

# Means with CIs taking clustering into account


## Create a table with all variables, their means, CIs and ICCs

```{r}

names <- df %>% select(-id, -intervention, -group, -school, -girl, -track) %>% names(.)

# model1 = lmer(paAccelerometer_T1 ~ (1|school) + (1|group) + b5open_T1.1, data=df)
# m_p <- profile(model1, which = "beta_")
# confint(m_p)

# Create empty soon-to-be-filled objects
m <- NA
mean <- NA
m_p <- NA
ci_low <- NA
ci_high <- NA
ICC_group <- NA
ICC_School <- NA
nonmissings <- NA

# Loop over each variable name, extract statistics: 

# all participants  
for (i in names){
m <- lmer(paste0(i," ~ (1|school) + (1|group)"), data=df)
mean[i] <- fixef(m)
m_p <- profile(m, which = "beta_")
ci_low[i] <- confint(m_p)[, 1]
ci_high[i] <- confint(m_p)[, 2]
ICC_group[i] <- icc(m)[1]
ICC_School[i] <- icc(m)[2]
nonmissings[i] <- length(m@resp$y)
}

# dftest <- df #%>% na.omit()
# m <- lmer(sitLieAccelerometer_diff ~ (1|school) + (1|group), data=dftest)
# mean <- fixef(m)
# m_p <- profile(m)
# ci_low <- confint(m_p)[, 1]
# ci_high <- confint(m_p)[, 2]
# ICC_group <- icc(m)[1]
# ICC_School <- icc(m)[2]
# nonmissings <- length(m@resp$y)



vardatatable <- data_frame(
  Variable = c(names(mean)), 
  Mean = round(mean, 2), 
  CI95 = paste(round(ci_low, 2), "-", round(ci_high, 2)), 
  "ICC class" =ifelse(round(ICC_group, 3) == 0, "< 0.001", round(ICC_group, 3)), 
  "ICC school" = ifelse(round(ICC_School, 3) == 0, "< 0.001", round(ICC_School, 3)),
  n = nonmissings) %>% 
  dplyr::arrange(Variable) %>% 
  filter(Variable != "") #remove first row, which is empty

options(tibble.print_max = 15)
 
# %>% 
#     apa_table(
#         caption = "",
#         note = "",
#         escape = T)
```

```{r}

vardatatable %>% select(Variable, `ICC class`, `ICC school`, n) %>% arrange(desc(`ICC class`)) %>% print(n = 20) %>% apa_table(caption = "Intra-class correlations sorted by class ICC")

```

```{r}

vardatatable %>% select(Variable, `ICC class`, `ICC school`, n) %>% arrange(desc(`ICC school`)) %>% print(n = 20) %>% apa_table(caption = "Intra-class correlations sorted by school ICC")

```


## Find ICC by educational track

## Create a table with all variables, their means, CIs and ICCs

```{r}
library(sjstats)
library(lme4)

names <- df %>% select(-id, -intervention, -group, -school, -girl, -track) %>% names(.)

# model1 = lmer(paAccelerometer_T1 ~ (1|school) + (1|group) + b5open_T1.1, data=df)
# m_p <- profile(model1, which = "beta_")
# confint(m_p)

# Create empty soon-to-be-filled objects
m <- NA
mean <- NA
m_p <- NA
ci_low <- NA
ci_high <- NA
ICC_group <- NA
ICC_School <- NA
nonmissings <- NA
ICC_track <- NA

# Loop over each variable name, extract statistics: 

# all participants  
for (i in names){
m <- lmer(paste0(i," ~ (1|school) + (1|group) + (1|track)"), data=df)
mean[i] <- fixef(m)
m_p <- profile(m, which = "beta_")
ci_low[i] <- confint(m_p)[5]
ci_high[i] <- confint(m_p)[10]
ICC_group[i] <- icc(m)[1]
ICC_School[i] <- icc(m)[3]
ICC_track[i] <- icc(m)[2]
nonmissings[i] <- length(m@resp$y)
}

# dftest <- df #%>% na.omit()
# m <- lmer(sitLieAccelerometer_T1 ~ (1|school) + (1|group) + (1|track), data=df)
# mean <- fixef(m)
# m_p <- profile(m)
# ci_low <- confint(m_p)[5]
# ci_high <- confint(m_p)[10]
# ICC_group <- icc(m)[1]
# ICC_School <- icc(m)[2]
# nonmissings <- length(m@resp$y)

vardatatable <- data_frame(
  Variable = c(names(mean)), 
  Mean = round(mean, 2), 
  CI95 = paste(round(ci_low, 2), "-", round(ci_high, 2)), 
  "ICC class" =ifelse(round(ICC_group, 3) == 0, "< 0.001", round(ICC_group, 3)), 
  "ICC school" = ifelse(round(ICC_School, 3) == 0, "< 0.001", round(ICC_School, 3)),
  "ICC educational track" = ifelse(round(ICC_track, 3) == 0, "< 0.001", round(ICC_track, 3)),
  n = nonmissings) %>% 
  dplyr::arrange(Variable) %>% 
  filter(Variable != "") #remove first row, which is empty

options(tibble.print_max = 15)
 
vardatatable %>% select(Variable, `ICC educational track`, `ICC class`, `ICC school`, n) %>% arrange(desc(`ICC educational track`)) %>% print(n = 20)

vardatatable %>% select(Variable, `ICC educational track`, `ICC class`, `ICC school`, n) %>% arrange(desc(`ICC class`)) %>% print(n = 20)

vardatatable %>% select(Variable, `ICC educational track`, `ICC class`, `ICC school`, n) %>% arrange(desc(`ICC school`)) %>% print(n = 20)
# %>% 
#     apa_table(
#         caption = "",
#         note = "",
#         escape = T)

```

```{r}

vardatatable %>% select(Variable, `ICC educational track`, `ICC class`, `ICC school`, n) %>% arrange(desc(`ICC educational track`)) %>% print(n = 20) %>%  apa_table(caption = "Intra-class correlations sorted by educational track ICC")

```


## Create a table for all items by gender and intervention allocation

```{r}
names <- df %>% select(-id, -intervention, -group, -school, -girl, -track) %>% names(.)

# Intercepts for boys; when boy is 1, girl is 0, but boy is a factor, so intercept is for boys even though boy is 1 for boys and 0 for girls.
m.boys <- NA
mean.boys <- NA
m_p.boys <- NA
ci_low.boys <- NA
ci_high.boys <- NA
ICC_group.boys <- NA
ICC_School.boys <- NA
nonmissings.boys <- NA

df.boys <- df %>% mutate(boy = factor(ifelse(girl == 1, 0, 1), levels = c(1, 0)))

for (i in names){
m.boys <- lmer(paste0(i," ~ (1|school) + (1|group) + boy"), data=df.boys)
mean.boys[i] <- fixef(m.boys)
m_p.boys <- profile(m.boys, which = "beta_")
ci_low.boys[i] <- confint(m_p.boys)[1, 1]
ci_high.boys[i] <- confint(m_p.boys)[1, 2]
ICC_group.boys[i] <- icc(m.boys)[1]
ICC_School.boys[i] <- icc(m.boys)[2]
nonmissings.boys[i] <- length(m.boys@resp$y)
}

cat("The labels are arranged such that intercept is not for girls:", labels(fixef(m.boys))[2] == "boy0")

ci_boys <- data.frame(ciLo = ci_low.boys, mean = mean.boys, ciHi = ci_high.boys)
diamondlabels <- labels(ci_boys)[[1]]
ci_boys <- data.frame(ci_boys, diamondlabels)

# Intercepts for girls; when boy is 1, girl is 0, but boy is a factor, so intercept is for girls even though girl is 1 for girls and 0 for boys.
m.girls <- NA
mean.girls <- NA
m_p.girls <- NA
ci_low.girls <- NA
ci_high.girls <- NA
ICC_group.girls <- NA
ICC_School.girls <- NA
nonmissings.girls <- NA

for (i in names){
m.girls <- lmer(paste0(i," ~ (1|school) + (1|group) + girl"), data=df)
mean.girls[i] <- fixef(m.girls)
m_p.girls <- profile(m.girls, which = "beta_")
ci_low.girls[i] <- confint(m_p.girls)[1, 1]
ci_high.girls[i] <- confint(m_p.girls)[1, 2]
ICC_group.girls[i] <- icc(m.girls)[1]
ICC_School.girls[i] <- icc(m.girls)[2]
nonmissings.girls[i] <- length(m.girls@resp$y)
}

cat("The labels are arranged such that intercept is not for boys:", labels(fixef(m.girls))[2] == "girl0")

ci_girls <- data.frame(ciLo = ci_low.girls, mean = mean.girls, ciHi = ci_high.girls)
diamondlabels <- labels(ci_girls)[[1]]
ci_girls <- data.frame(ci_girls, diamondlabels)


# Intercepts for intervention
m.intervention <- NA
mean.intervention <- NA
m_p.intervention <- NA
ci_low.intervention <- NA
ci_high.intervention <- NA
ICC_group.intervention <- NA
ICC_School.intervention <- NA
nonmissings.intervention <- NA

## change "intervention" to be consistent regarding level order with "girl".
df.intervention <- df %>% mutate(intervention = factor(intervention, levels = c(1, 0)))

for (i in names){
m.intervention <- lmer(paste0(i," ~ (1|school) + (1|group) + intervention"), data=df.intervention)
mean.intervention[i] <- fixef(m.intervention)
m_p.intervention <- profile(m.intervention, which = "beta_")
ci_low.intervention[i] <- confint(m_p.intervention)[1, 1]
ci_high.intervention[i] <- confint(m_p.intervention)[1, 2]
ICC_group.intervention[i] <- icc(m.intervention)[1]
ICC_School.intervention[i] <- icc(m.intervention)[2]
nonmissings.intervention[i] <- length(m.intervention@resp$y)
}

cat("The labels are arranged such that intercept is not for control:", labels(fixef(m.intervention))[2] == "intervention0")

ci_intervention <- data.frame(ciLo = ci_low.intervention, mean = mean.intervention, ciHi = ci_high.intervention)
diamondlabels <- labels(ci_intervention)[[1]]
ci_intervention <- data.frame(ci_intervention, diamondlabels)

# Intercepts for control

m.control <- NA
mean.control <- NA
m_p.control <- NA
ci_low.control <- NA
ci_high.control <- NA
ICC_group.control <- NA
ICC_School.control <- NA
nonmissings.control <- NA

df.control <- df %>% mutate(control = factor(ifelse(intervention == 1, 0, 1), levels = c(1, 0)))

for (i in names){
m.control <- lmer(paste0(i," ~ (1|school) + (1|group) + control"), data=df.control)
mean.control[i] <- fixef(m.control)
m_p.control <- profile(m.control, which = "beta_")
ci_low.control[i] <- confint(m_p.control)[1, 1]
ci_high.control[i] <- confint(m_p.control)[1, 2]
ICC_group.control[i] <- icc(m.control)[1]
ICC_School.control[i] <- icc(m.control)[2]
nonmissings.control[i] <- length(m.control@resp$y)
}

cat("The labels are arranged such that intercept is not for intervention:", labels(fixef(m.control))[2] == "control0")

ci_control <- data.frame(ciLo = ci_low.control, mean = mean.control, ciHi = ci_high.control)
diamondlabels <- labels(ci_control)[[1]]
ci_control <- data.frame(ci_control, diamondlabels)

# Same ICC results you'd get with e.g.:
# m1 <- as.data.frame(VarCorr(m))
# m1$vcov[1] / (m1$vcov[1] + m1$vcov[3])

# Or from broom:
# tidy(m)$estimate[2]^2 / (tidy(m)$estimate[2]^2 + tidy(m)$estimate[4]^2)

# Or from sjstats:
# sum(get_re_var(m)) / (sum(get_re_var(m)) + get_re_var(m, "sigma_2"))


```

# Descriptive tables

## prepare data

```{r demographics-prep}

demographics <- lmi %>% dplyr::select(id = ID,
birthYear = Kys0004.1,
intervention = ryhmä,
school = Aineisto.1,
girl = Kys0013.1,
ethnicity = Kys0005.1,
studyYear = Kys0014.1) %>% 
  mutate(age = 2016 - birthYear,
         intervention = ifelse(intervention == 1, 1, 0),
         intervention = as.numeric(intervention),
         girl = ifelse(girl == 2, 1, 0),
          girl = as.numeric(girl, levels = c("1", "0")),
         school = factor(school, levels = c("1", "2", "3", "4", "5")),
         bornInFinland = as.numeric(ifelse(ethnicity == 1, 1, 0)),
         studyYear = ifelse(studyYear == 0, NA, studyYear)) # Remove "other" from study year

# Insert track variable with those who answered "other" with one of the actual category labels given the appropriate category:
Track <- lmi %>% select(Kys0016.1, Kys0017.1) %>% mutate(
  Kys0016.1 = ifelse(Kys0017.1 == "Merkonomi" | Kys0017.1 == "merkonomi", 3,
                  ifelse(Kys0017.1 == "Datanomi" | Kys0017.1 == "datanomi", 2, Kys0016.1)),
  Track = factor(Kys0016.1, # Fix track labels first
                     levels = c(0, 1, 2, 3, 4),
                     labels = c("Other", "Business IT", "Business Admin", "HRC", "Nursing"))) %>% 
  select(-Kys0016.1, -Kys0017.1)

demographics <- bind_cols(demographics, Track)
```

## Create demographic tables

### By educational track

```{r demographics-table-track, results = 'asis'}
demotable <- demographics %>% 
  group_by(Track) %>% 
  summarise("Mean age (range)" = paste0(round(mean(age, na.rm = T), 1)," (", 
                                        range(age, na.rm = T)[1], "-",
                                        range(age, na.rm = T)[2], ")"),
            "Mean study year (sd)" = paste0(round(mean(studyYear, na.rm = T), 1)," (", 
                                               round(sd(studyYear, na.rm = T), 1), ")"),
            "% girl" = round(mean(girl, na.rm = T)*100, 1),
            "% intervention" = round(mean(intervention, na.rm = T)*100, 1),
            "% born in Finland" = round(mean(bornInFinland, na.rm = T)*100, 1),
            n = n()) %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(Track)) 

demotable_total <- demographics %>% 
  summarise("Track" = "Total",
            "Mean age (range)" = paste0(round(mean(age, na.rm = T), 1)," (", 
                                        range(age, na.rm = T)[1], "-",
                                        range(age, na.rm = T)[2], ")"),
            "Mean study year (sd)" = paste0(round(mean(studyYear, na.rm = T), 1)," (", 
                                               round(sd(studyYear, na.rm = T), 1), ")"),
            "% girl" = round(mean(girl, na.rm = T)*100, 1),
            "% intervention" = round(mean(intervention, na.rm = T)*100, 1),
            "% born in Finland" = round(mean(bornInFinland, na.rm = T)*100, 1),
            n = n())

demotable <- bind_rows(demotable, demotable_total)

demotable <- demotable %>% gather(var, val, 2:ncol(demotable)) %>% spread(Track, val)

# For some reason, sum of n's of all tracks is 1084.

apa_table(demotable, caption = "Baseline demographics of educational tracks", digits = c(0, 1, 1, 1, 1, 1, 0))
```

### By gender

```{r demographics-table-gender, results = 'asis'}
demographics$Girl <- factor(demographics$girl)

demotable <- demographics %>% 
  group_by(Girl) %>% 
  summarise("Mean age (range)" = paste0(round(mean(age, na.rm = T), 1)," (", 
                                        range(age, na.rm = T)[1], "-",
                                        range(age, na.rm = T)[2], ")"),
            "Mean study year (sd)" = paste0(round(mean(studyYear, na.rm = T), 1)," (", 
                                               round(sd(studyYear, na.rm = T), 1), ")"),
            "% intervention" = round(mean(intervention, na.rm = T)*100, 1),
            "% born in Finland" = round(mean(bornInFinland, na.rm = T)*100, 1),
            n = n()) %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(Girl)) 

demotable_total <- demographics %>% 
  summarise("Girl" = "Total",
            "Mean age (range)" = paste0(round(mean(age, na.rm = T), 1)," (", 
                                        range(age, na.rm = T)[1], "-",
                                        range(age, na.rm = T)[2], ")"),
            "Mean study year (sd)" = paste0(round(mean(studyYear, na.rm = T), 1)," (", 
                                               round(sd(studyYear, na.rm = T), 1), ")"),
            "% intervention" = round(mean(intervention, na.rm = T)*100, 1),
            "% born in Finland" = round(mean(bornInFinland, na.rm = T)*100, 1),
            n = n())

demotable <- bind_rows(demotable, demotable_total)

demotable <- demotable %>% gather(var, val, 2:ncol(demotable)) %>% spread(girl, val)

# For some reason, sum of n's of all tracks is 1084.

apa_table(demotable, caption = "Baseline demographics of educational tracks", digits = c(0, 1, 1, 1, 1, 0))
```

### By intervention participation

```{r demographics-table-intervention, results = 'asis'}
demographics$intervention <- factor(demographics$intervention)
demographics$girl <- as.numeric(demographics$girl)

demotable <- demographics %>% 
  group_by(intervention) %>% 
  summarise("Mean age (range)" = paste0(round(mean(age, na.rm = T), 1)," (", 
                                        range(age, na.rm = T)[1], "-",
                                        range(age, na.rm = T)[2], ")"),
            "Mean study year (sd)" = paste0(round(mean(studyYear, na.rm = T), 1)," (", 
                                               round(sd(studyYear, na.rm = T), 1), ")"),
            "% girl" = round(mean(girl, na.rm = T)*100, 1),
            "% born in Finland" = round(mean(bornInFinland, na.rm = T)*100, 1),
            n = n()) %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(intervention)) 

demotable_total <- demographics %>% 
  summarise("intervention" = "Total",
            "Mean age (range)" = paste0(round(mean(age, na.rm = T), 1)," (", 
                                        range(age, na.rm = T)[1], "-",
                                        range(age, na.rm = T)[2], ")"),
            "Mean study year (sd)" = paste0(round(mean(studyYear, na.rm = T), 1)," (", 
                                               round(sd(studyYear, na.rm = T), 1), ")"),
            "% girl" = round(mean(girl, na.rm = T)*100, 1),
            "% born in Finland" = round(mean(bornInFinland, na.rm = T)*100, 1),
            n = n())

demotable <- bind_rows(demotable, demotable_total)

demotable <- demotable %>% gather(var, val, 2:ncol(demotable)) %>% spread(intervention, val)

# For some reason, sum of n's of all tracks is 1084.

apa_table(demotable, caption = "Baseline demographics of educational tracks", digits = c(0, 1, 1, 1, 1, 0))
```

## Create outcome tables

### By educational track

```{r outcome-table, results = 'asis'}
outtable <- df %>%
  select(paAccelerometer_T1, sitLieAccelerometer_T1, sitBreaks_T1, fatpct_T1, track) %>% 
  group_by(track) %>% 
  summarise("Mean daily MVPA minutes (sd)" = paste0(round(mean(paAccelerometer_T1, na.rm = T), 1)," (", 
                                        round(sd(paAccelerometer_T1, na.rm = T), 1), ")"),
            "Mean daily minutes spent sitting or lying down (sd)" = paste0(round(mean(sitLieAccelerometer_T1, na.rm = T), 1)," (", 
                                        round(sd(sitLieAccelerometer_T1, na.rm = T), 1), ")"),
            "Mean daily breaks in sitting (sd)" = paste0(round(mean(fatpct_T1, na.rm = T), 1)," (", 
                                        round(sd(fatpct_T1, na.rm = T), 1), ")"),
            "Mean fat-% (sd)" = paste0(round(mean(sitBreaks_T1, na.rm = T), 1)," (", 
                                        round(sd(sitBreaks_T1, na.rm = T), 1), ")"),
            n = n()) %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(track)) 

outtable_total <- df %>% 
  summarise("track" = "Total",
            "Mean daily MVPA minutes (sd)" = paste0(round(mean(paAccelerometer_T1, na.rm = T), 1)," (", 
                                        round(sd(paAccelerometer_T1, na.rm = T), 1), ")"),
            "Mean daily minutes spent sitting or lying down (sd)" = paste0(round(mean(sitLieAccelerometer_T1, na.rm = T), 1)," (", 
                                        round(sd(sitLieAccelerometer_T1, na.rm = T), 1), ")"),
            "Mean daily breaks in sitting (sd)" = paste0(round(mean(fatpct_T1, na.rm = T), 1)," (", 
                                        round(sd(fatpct_T1, na.rm = T), 1), ")"),
            "Mean fat-% (sd)" = paste0(round(mean(sitBreaks_T1, na.rm = T), 1)," (", 
                                        round(sd(sitBreaks_T1, na.rm = T), 1), ")"),
            n = n())



outtable1 <- bind_rows(outtable, outtable_total)
outtable1 <- outtable1 %>% gather(var, val, 2:ncol(outtable1)) %>% spread(track, val)

apa_table(outtable1, caption = "Baseline demographics of educational tracks", digits = c(0, 1, 1, 1, 1, 0))


```

# Diamond plots

## PA psychosocial determinants: self report scales T1

```{r}
PA_ci_girls <- ci_girls %>% filter(diamondlabels %in% names(scales_T1) & grepl("PA_", diamondlabels) & !grepl("bct", diamondlabels))

PA_ci_boys <- ci_boys %>% filter(diamondlabels %in% names(scales_T1) & grepl("PA_", diamondlabels) & !grepl("bct", diamondlabels))

PA_ci_intervention <- ci_intervention %>% filter(diamondlabels %in% names(scales_T1) & grepl("PA_", diamondlabels) & !grepl("bct", diamondlabels))

PA_ci_control <- ci_control %>% filter(diamondlabels %in% names(scales_T1) & grepl("PA_", diamondlabels) & !grepl("bct", diamondlabels))

ICClabels <- vardatatable %>% filter(Variable %in% PA_ci_control$diamondlabels)

plot1 <- diamondPlot(PA_ci_girls, color = 'green', alpha=.3, yLabels = PA_ci_girls$diamondlabels, fixedSize = 0.3, xlab = NULL) +
  diamondPlot(PA_ci_boys, returnLayerOnly = TRUE, color='blue', alpha=.3, fixedSize = 0.3) +
  scale_x_continuous(limits = c(1, 7), breaks = 1:7)

plot2 <- diamondPlot(PA_ci_intervention, color = 'red', alpha=.3, yLabels = c(rep("", length(PA_ci_girls$diamondlabels))), fixedSize = 0.3, xlab = NULL, ylab = NULL) +
  diamondPlot(PA_ci_control, returnLayerOnly = TRUE, color='black', alpha=.3, fixedSize = 0.3) +
  scale_x_continuous(limits = c(1, 7), breaks = 1:7)

grid.newpage()
grid.draw(cbind(ggplotGrob(plot1), ggplotGrob(plot2), size = "first"))
# dat2 <- data.frame(ciLo = c(3, 2), mean = c(4, 2.5), ciHi = c(6, 3));
# diamondPlot(dat1, color = 'blue', alpha=.3, yLabels = dat1$diamondlabels) +
# diamondPlot(dat2, returnLayerOnly = TRUE, color='red', alpha=.3)

```

Note: action and coping planning on a scale from 1 to 4.

# Ridge plots

## PA motivation

```{r}

plot1 <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
  'PA autonomous \nmotivation' = PA_autonomous_T1,
'PA controlled \nmotivation' = PA_controlled_T1,
'PA amotivation' = PA_amotivation_T1)  %>%
  # select(noquote(order(colnames(.)))) %>% # Orders columns alphabetically
  gather(key = Variable, value = Value, 6:ncol(.)) %>% 
  ggplot(aes(y = Variable)) +
  geom_density_ridges(aes(x = Value, fill = paste(Variable, girl)), 
           alpha = .6, color = "black", from = 1, to = 7) +
  labs(x = "",
       y = "") +
  scale_y_discrete(expand = c(0.01, 0)) +
  scale_x_continuous(expand = c(0.01, 0)) +
  scale_fill_cyclical(breaks = c("PA amotivation 0", "PA amotivation 1"),
                      labels = c( 'PA amotivation 0' = "Boy", 'PA amotivation 1' = "Girl"),
                      values = c("#3bc600", "#0000ff", "#9cc68b", "#8080ff"),
                      name = "", guide = "legend") +
  theme_ridges(grid = FALSE) +
  theme(legend.position="bottom")

plot2 <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
  'PA autonomous motivation' = PA_autonomous_T1,
'PA controlled motivation' = PA_controlled_T1,
'PA amotivation' = PA_amotivation_T1) %>%
  # select(noquote(order(colnames(.)))) %>% # Orders columns alphabetically
  gather(key = Variable, value = Value, 6:ncol(.)) %>% 
  ggplot(aes(y = Variable)) +
  geom_density_ridges(aes(x = Value, fill = paste(Variable, intervention)), 
           alpha = .6, color = "black", from = 1, to = 7) +
  labs(x = "",
       y = "") +
  scale_y_discrete(expand = c(0.01, 0), labels = NULL) +
  scale_x_continuous(expand = c(0.01, 0)) +
  scale_fill_cyclical(breaks = c("PA amotivation 1", "PA amotivation 0"),
                      labels = c('PA amotivation 1' = "Intervention", 'PA amotivation 0' = "Control"),
                      values = c("#ff0000", "#0000ff", "#ff8080", "#8080ff"),
                      name = "", guide = "legend") +
  theme_ridges(grid = FALSE) +
  theme(legend.position="bottom")

# grid.arrange(plot1, plot2, ncol = 2)

grid.newpage()
grid.draw(cbind(ggplotGrob(plot1), ggplotGrob(plot2), size = "first"))
```

## Big 5 personality traits

```{r}

plot1 <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'Agreeableness' = b5agr_T1,
'Conscientiousness' = b5cons_T1,
'Extraversion' = b5ext_T1,
'Neuroticism' = b5neur_T1,
'Openness' = b5open_T1)  %>%
  # select(noquote(order(colnames(.)))) %>% # Orders columns alphabetically
  gather(key = Variable, value = Value, 6:ncol(.)) %>% 
  ggplot(aes(y = Variable)) +
  geom_density_ridges(aes(x = Value, fill = paste(Variable, girl)), 
           alpha = .6, color = "black", from = 1, to = 7) +
  labs(x = "",
       y = "") +
  scale_y_discrete(expand = c(0.01, 0)) +
  scale_x_continuous(expand = c(0.01, 0)) +
  scale_fill_cyclical(breaks = c("Agreeableness 0", "Agreeableness 1"),
                      labels = c( 'Agreeableness 0' = "Boy", 'Agreeableness 1' = "Girl"),
                      values = c("#3bc600", "#0000ff", "#9cc68b", "#8080ff"),
                      name = "", guide = "legend") +
  theme_ridges(grid = FALSE) +
  theme(legend.position="bottom")

plot2 <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'Agreeableness' = b5agr_T1,
'Conscientiousness' = b5cons_T1,
'Extraversion' = b5ext_T1,
'Neuroticism' = b5neur_T1,
'Openness' = b5open_T1) %>%
  # select(noquote(order(colnames(.)))) %>% # Orders columns alphabetically
  gather(key = Variable, value = Value, 6:ncol(.)) %>% 
  ggplot(aes(y = Variable)) +
  geom_density_ridges(aes(x = Value, fill = paste(Variable, intervention)), 
           alpha = .6, color = "black", from = 1, to = 7) +
  labs(x = "",
       y = "") +
  scale_y_discrete(expand = c(0.01, 0), labels = NULL) +
  scale_x_continuous(expand = c(0.01, 0)) +
  scale_fill_cyclical(breaks = c("Agreeableness 1", "Agreeableness 0"),
                      labels = c('Agreeableness 1' = "Intervention", 'Agreeableness 0' = "Control"),
                      values = c("#ff0000", "#0000ff", "#ff8080", "#8080ff"),
                      name = "", guide = "legend") +
  theme_ridges(grid = FALSE) +
  theme(legend.position="bottom")

# grid.arrange(plot1, plot2, ncol = 2)

grid.newpage()
grid.draw(cbind(ggplotGrob(plot1), ggplotGrob(plot2), size = "first"))
```

## BCT use

### Ridge plots for means

```{r}

plot1 <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'Frequency-\nrelated BCTs' = PA_frqbct_T1,
'Agreement-\nrelated BCTs' = PA_agrbct_T1)  %>%
  # select(noquote(order(colnames(.)))) %>% # Orders columns alphabetically
  gather(key = Variable, value = Value, 6:ncol(.)) %>% 
  ggplot(aes(y = Variable)) +
  geom_density_ridges(aes(x = Value, fill = paste(Variable, girl)), 
           alpha = .6, color = "black", from = 1, to = 7) +
  labs(x = "",
       y = "") +
  scale_y_discrete(expand = c(0.01, 0)) +
  scale_x_continuous(expand = c(0.01, 0)) +
  scale_fill_cyclical(breaks = c("Agreement-\nrelated BCTs 0", "Agreement-\nrelated BCTs 1"),
                      labels = c( 'Agreement-\nrelated BCTs 0' = "Boy", 'Agreement-\nrelated BCTs 1' = "Girl"),
                      values = c("#3bc600", "#0000ff", "#9cc68b", "#8080ff"),
                      name = "", guide = "legend") +
  theme_ridges(grid = FALSE) +
  theme(legend.position="bottom")

plot2 <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'Frequency-\nrelated BCTs' = PA_frqbct_T1,
'Agreement-\nrelated BCTs' = PA_agrbct_T1) %>%
  # select(noquote(order(colnames(.)))) %>% # Orders columns alphabetically
  gather(key = Variable, value = Value, 6:ncol(.)) %>% 
  ggplot(aes(y = Variable)) +
  geom_density_ridges(aes(x = Value, fill = paste(Variable, intervention)), 
           alpha = .6, color = "black", from = 1, to = 7) +
  labs(x = "",
       y = "") +
  scale_y_discrete(expand = c(0.01, 0), labels = NULL) +
  scale_x_continuous(expand = c(0.01, 0)) +
  scale_fill_cyclical(breaks = c("Agreement-\nrelated BCTs 1", "Agreement-\nrelated BCTs 0"),
                      labels = c('Agreement-\nrelated BCTs 1' = "Intervention", 'Agreement-\nrelated BCTs 0' = "Control"),
                      values = c("#ff0000", "#0000ff", "#ff8080", "#8080ff"),
                      name = "", guide = "legend") +
  theme_ridges(grid = FALSE) +
  theme(legend.position="bottom")

grid.newpage()
grid.draw(cbind(ggplotGrob(plot1), ggplotGrob(plot2), size = "first"))



# grid.arrange(plot1, plot2, ncol = 2)

```



### sm kernel density plots for means

#### Frequency-measured BCTs

```{r}

colfill <- c(1,2,3,4,5)

# Create data frame
densplot <- df
levels(densplot$intervention) <- list("Intervention" = "1", "Control" = "0")
levels(densplot$girl) <- list("Girl" = "1", "Boy" = "0")

# This gives side-by-side plots
 layout(matrix(c(1,2,3,3), nrow = 2, ncol = 2, byrow = TRUE), heights=c(2.5, 2))

## Intervention vs. control
# Choose only the variables needed and drop NA
dens <- densplot %>% select(PA_frqbct_T1, intervention) %>% 
  na.omit(.)

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Make plot
sm.PA_frqbct_T1_1 <- sm.density.compare2(as.numeric(dens$PA_frqbct_T1), as.factor(dens$intervention), xlab="", col=colfill, lty=c(1,2), bandcol='LightGray', model="equal", lwd=(c(2,2)))
legend("topright", levels(dens$intervention), fill=c(1, 2))

## Girls vs. boys
# Choose only the variables needed and drop NA
dens <- densplot %>% select(PA_frqbct_T1, girl) %>% 
  na.omit(.)

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Make plot
sm.PA_frqbct_T1_2 <- sm.density.compare2(as.numeric(dens$PA_frqbct_T1), as.factor(dens$girl), xlab="", col=colfill, lty=c(1,2), bandcol='LightGray', model="equal", lwd=(c(2,2)))
legend("topright", levels(dens$girl), fill=c(1, 2))

## Differences in schools
# Choose only the variables needed and drop NA
dens <- densplot %>% select(PA_frqbct_T1, school) %>% 
  na.omit(.)

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Intervention groups with solid thicker lines
linetypes <- c(1,2,2,1,2)

# Make plot
sm.PA_frqbct_T1_3 <- sm.density.compare(as.numeric(dens$PA_frqbct_T1), dens$school, xlab="", col=colfill, lty=linetypes, model="none")
legend("topright", c("Intervention school", "Control school"), col = c(4, 3), lty = c(1, 2), lwd = c(2, 2))

```

#### Agreement-measured BCTs

```{r}

colfill <- c(1,2,3,4,5)

# Create data frame
densplot <- df
levels(densplot$intervention) <- list("Intervention" = "1", "Control" = "0")
levels(densplot$girl) <- list("Girl" = "1", "Boy" = "0")

# This gives side-by-side plots
 layout(matrix(c(1,2,3,3), nrow = 2, ncol = 2, byrow = TRUE), heights=c(2.5, 2))

## Intervention vs. control
# Choose only the variables needed and drop NA
dens <- densplot %>% select(PA_agrbct_T1, intervention) %>% 
  na.omit(.)

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Make plot
sm.PA_agrbct_T1_1 <- sm.density.compare2(as.numeric(dens$PA_agrbct_T1), as.factor(dens$intervention), xlab="", col=colfill, lty=c(1,2), bandcol='LightGray', model="equal", lwd=(c(2,2)))
legend("topright", levels(dens$intervention), fill=c(1, 2))

## Girls vs. boys
# Choose only the variables needed and drop NA
dens <- densplot %>% select(PA_agrbct_T1, girl) %>% 
  na.omit(.)

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Make plot
sm.PA_agrbct_T1_2 <- sm.density.compare2(as.numeric(dens$PA_agrbct_T1), as.factor(dens$girl), xlab="", col=colfill, lty=c(1,2), bandcol='LightGray', model="equal", lwd=(c(2,2)))
legend("topright", levels(dens$girl), fill=c(1, 2))

## Differences in schools
# Choose only the variables needed and drop NA
dens <- densplot %>% select(PA_agrbct_T1, school) %>% 
  na.omit(.)

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Intervention groups with solid thicker lines
linetypes <- c(1,2,2,1,2)

# Make plot
sm.PA_agrbct_T1_3 <- sm.density.compare(as.numeric(dens$PA_agrbct_T1), dens$school, xlab="", col=colfill, lty=linetypes, model="none")
legend("topright", c("Intervention school", "Control school"), col = c(4, 3), lty = c(1, 2), lwd = c(2, 2))

```

### Histograms for individual items

#### Frequency-measured BCTs

These questions were asked with the lead "Have you done the following during the last three weeks?". 

The answer scale was as follows:

0 = not once
1 = once
2 = twice
3 = weekly
4 = about every second day
5 = daily

Items are as follows: 

I have reminded myself even in my spare time, what kind of positive consequences frequent PA would have in my life.
I have monitored my PA by marking the PA occasions on an exercise log on paper.
I have monitored my PA by using a smart phone, e.g. the Moves-app.
I use mnemonic cues with which I remember to implement my PA intention.
I have compared my actualized PA with the PA goal I have set.
I have thought about which reasons to do PA are important to me personally.
I have made changes in my home (e.g. my room or my computer), so that starting PA would be easier.
I have asked my friends or family for support to reach my PA goals.
If I haven't reached my PA goal, I have evaluated, what went wrong.

```{r}

bctGirls <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'Reminded self of positive consequences' = PA_frqbct_01_T1,
'Has logged PA on paper' = PA_frqbct_02_T1,
'Has monitored PA on smartphone' = PA_frqbct_03_T1,
'Uses mnemonic cues' = PA_frqbct_04_T1,
'Has compared actual with goal' = PA_frqbct_05_T1,
'Has thought of relevance of PA' = PA_frqbct_06_T1,
'Has made changes at home' = PA_frqbct_07_T1,
'Has sought social support' = PA_frqbct_08_T1,
'Has evaluated why goal not reached' = PA_frqbct_09_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(girl == "1") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:6), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("darkolivegreen2", "darkolivegreen4")) +
  labs(title = "Girls") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 6.5))

bctBoys <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'Reminded self of positive consequences' = PA_frqbct_01_T1,
'Has logged PA on paper' = PA_frqbct_02_T1,
'Has monitored PA on smartphone' = PA_frqbct_03_T1,
'Uses mnemonic cues' = PA_frqbct_04_T1,
'Has compared actual with goal' = PA_frqbct_05_T1,
'Has thought of relevance of PA' = PA_frqbct_06_T1,
'Has made changes at home' = PA_frqbct_07_T1,
'Has sought social support' = PA_frqbct_08_T1,
'Has evaluated why goal not reached' = PA_frqbct_09_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(girl == "0") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:6), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("darkolivegreen2", "darkolivegreen4")) +
  labs(title = "Boys") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 6.5))

bctInt <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'Reminded self of positive consequences' = PA_frqbct_01_T1,
'Has logged PA on paper' = PA_frqbct_02_T1,
'Has monitored PA on smartphone' = PA_frqbct_03_T1,
'Uses mnemonic cues' = PA_frqbct_04_T1,
'Has compared actual with goal' = PA_frqbct_05_T1,
'Has thought of relevance of PA' = PA_frqbct_06_T1,
'Has made changes at home' = PA_frqbct_07_T1,
'Has sought social support' = PA_frqbct_08_T1,
'Has evaluated why goal not reached' = PA_frqbct_09_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(intervention == "1") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:6), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "") +
  scale_fill_cyclical(values = c("deepskyblue", "deepskyblue4")) +
  labs(title = "Intervention") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 6.5))

bctCont <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'Reminded self of positive consequences' = PA_frqbct_01_T1,
'Has logged PA on paper' = PA_frqbct_02_T1,
'Has monitored PA on smartphone' = PA_frqbct_03_T1,
'Uses mnemonic cues' = PA_frqbct_04_T1,
'Has compared actual with goal' = PA_frqbct_05_T1,
'Has thought of relevance of PA' = PA_frqbct_06_T1,
'Has made changes at home' = PA_frqbct_07_T1,
'Has sought social support' = PA_frqbct_08_T1,
'Has evaluated why goal not reached' = PA_frqbct_09_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(intervention == "0") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:6), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("deepskyblue", "deepskyblue4")) +
  labs(title = "Control") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 6.5))

#grid.arrange(bctInt, bctGirls, bctCont, bctBoys, ncol = 2)

# ("Seldom or never", "About once a month", "About once a week", "Almost daily")

# This draws all histograms next to each other:
grid.newpage()
grid.draw(cbind(ggplotGrob(bctInt), ggplotGrob(bctCont), ggplotGrob(bctGirls), ggplotGrob(bctBoys), size = "last"))

# This draws 2 histograms per row:
# grid.newpage()
# grid.draw(rbind(cbind(ggplotGrob(bctInt), ggplotGrob(bctCont), size = "last"), cbind(ggplotGrob(bctGirls), ggplotGrob(bctBoys), size = "last")))

```


#### Agreement-measured BCTs

These questions were asked with the lead "Have you done the following during the last three weeks?". 

The answer scale was as follows:

0 = not at all true
1 ... 4 [unlabeled]
5 = completely true

Items are as follows: 

I have set PA goals for myself.
I have personally made a specific plan ("what, where, how") to implement my PA.
I have a PA plan, which has been made by someone else, e.g. my sports club (e.g. a workout schedule).
I have a way by which I remind myself of my PA plan, e.g. I write it down in the calendar.
I have cut larger PA goals to smaller subgoals.
I have tried out new ways for me to be physically active.
I have pondered, what kind of difficult situations or barriers prevent me from implementing my PA plan.
I have planned for ways to overcome barriers to doing PA.
I have thought about how PA fits my identity (self concept).
I have attempted to find ways to exercise so, that it won't obstruct but instead helps actualise my other life values.


```{r}
p_load(grid)

bctGirls <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
  'Has set goals' = PA_agrbct_01_T1,
  'Has made plan' = PA_agrbct_02_T1,
  'Plan made by other' = PA_agrbct_03_T1,
  'Has reminder of plan' = PA_agrbct_04_T1,
  'Has cut goals to subgoals' = PA_agrbct_05_T1,
  'Has tried new PA options' = PA_agrbct_06_T1,
  'Has thought of barriers' = PA_agrbct_07_T1,
  'Has planned for barriers' = PA_agrbct_08_T1,
  'Has thought of PA identity' = PA_agrbct_09_T1,
  'Has fitted PA to life values' = PA_agrbct_10_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(girl == "1") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:6), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("darkolivegreen2", "darkolivegreen4")) +
  labs(title = "Girls") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 6.5))

bctBoys <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
  'Has set goals' = PA_agrbct_01_T1,
  'Has made plan' = PA_agrbct_02_T1,
  'Plan made by other' = PA_agrbct_03_T1,
  'Has reminder of plan' = PA_agrbct_04_T1,
  'Has cut goals to subgoals' = PA_agrbct_05_T1,
  'Has tried new PA options' = PA_agrbct_06_T1,
  'Has thought of barriers' = PA_agrbct_07_T1,
  'Has planned for barriers' = PA_agrbct_08_T1,
  'Has thought of PA identity' = PA_agrbct_09_T1,
  'Has fitted PA to life values' = PA_agrbct_10_T1) %>%
  gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(girl == "0") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:6), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("darkolivegreen2", "darkolivegreen4")) +
  labs(title = "Boys") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 6.5))

bctInt <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
  'Has set goals' = PA_agrbct_01_T1,
  'Has made plan' = PA_agrbct_02_T1,
  'Plan made by other' = PA_agrbct_03_T1,
  'Has reminder of plan' = PA_agrbct_04_T1,
  'Has cut goals to subgoals' = PA_agrbct_05_T1,
  'Has tried new PA options' = PA_agrbct_06_T1,
  'Has thought of barriers' = PA_agrbct_07_T1,
  'Has planned for barriers' = PA_agrbct_08_T1,
  'Has thought of PA identity' = PA_agrbct_09_T1,
  'Has fitted PA to life values' = PA_agrbct_10_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(intervention == "1") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:6), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "") +
  scale_fill_cyclical(values = c("deepskyblue", "deepskyblue4")) +
  labs(title = "Intervention") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 6.5))

bctCont <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
  'Has set goals' = PA_agrbct_01_T1,
  'Has made plan' = PA_agrbct_02_T1,
  'Plan made by other' = PA_agrbct_03_T1,
  'Has reminder of plan' = PA_agrbct_04_T1,
  'Has cut goals to subgoals' = PA_agrbct_05_T1,
  'Has tried new PA options' = PA_agrbct_06_T1,
  'Has thought of barriers' = PA_agrbct_07_T1,
  'Has planned for barriers' = PA_agrbct_08_T1,
  'Has thought of PA identity' = PA_agrbct_09_T1,
  'Has fitted PA to life values' = PA_agrbct_10_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(intervention == "0") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:6), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("deepskyblue", "deepskyblue4")) +
  labs(title = "Control") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 6.5))

#grid.arrange(bctInt, bctGirls, bctCont, bctBoys, ncol = 2)

# ("Seldom or never", "About once a month", "About once a week", "Almost daily")

# This draws all histograms next to each other:
grid.newpage()
grid.draw(cbind(ggplotGrob(bctInt), ggplotGrob(bctCont), ggplotGrob(bctGirls), ggplotGrob(bctBoys), size = "last"))

# This draws 2 histograms per row:
# grid.newpage()
# grid.draw(rbind(cbind(ggplotGrob(bctInt), ggplotGrob(bctCont), size = "last"), cbind(ggplotGrob(bctGirls), ggplotGrob(bctBoys), size = "last")))

# bctBoys <- df %>% dplyr::select(id,
#   intervention,
#   group,
#   school,
#   girl,
#   'Has set goals' = PA_agrbct_01_T1,
#   'Has made plan' = PA_agrbct_02_T1,
#   'Plan made by other' = PA_agrbct_03_T1,
#   'Has reminder of plan' = PA_agrbct_04_T1,
#   'Has cut goals to subgoals' = PA_agrbct_05_T1,
#   'Has tried new PA options' = PA_agrbct_06_T1,
#   'Has thought of barriers' = PA_agrbct_07_T1,
#   'Has planned for barriers' = PA_agrbct_08_T1,
#   'Has thought of PA identity' = PA_agrbct_09_T1,
#   'Has fitted PA to life values' = PA_agrbct_10_T1)
# 
# mean(bctBoys$`Has set goals`, na.rm = T)
# mean(bctBoys$`Has made plan`, na.rm = T)
# mean(bctBoys$`Plan made by other`, na.rm = T)
# mean(bctBoys$`Has reminder of plan`, na.rm = T)
# mean(bctBoys$`Has cut goals to subgoals`, na.rm = T)
# mean(bctBoys$`Has tried new PA options`, na.rm = T)
# mean(bctBoys$`Has thought of barriers`, na.rm = T)
# mean(bctBoys$`Has planned for barriers`, na.rm = T)
# mean(bctBoys$`Has thought of PA identity`, na.rm = T)
# mean(bctBoys$`Has fitted PA to life values`, na.rm = T)
```



## PA determinants

```{r}

plot1 <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'PA action and\ncoping planning' = PA_actCop_T1,
'PA intention' = PA_intention_T1,
'PA outcome\nexpectations' = PA_oexp_T1,
'PA perceived\nbehavioural control' = PA_pbc_T1,
'PA self efficacy' = PA_selfefficacy_T1,
'PA perceived\nopportunities' = PA_opportunities_T1,
'PA descriptive\nnorm' = PA_dnorm_T1,
'PA injunctive\nnorm' = PA_inorm_T1)  %>%
  # select(noquote(order(colnames(.)))) %>% # Orders columns alphabetically
  gather(key = Variable, value = Value, 6:ncol(.), factor_key = TRUE) %>% 
  ggplot(aes(y = Variable)) +
  geom_density_ridges(aes(x = Value, fill = paste(Variable, girl)), 
           alpha = .6, color = "black", from = 1, to = 7) +
  labs(x = "",
       y = "") +
  scale_y_discrete(expand = c(0.01, 0)) +
  scale_x_continuous(expand = c(0.01, 0)) +
  scale_fill_cyclical(breaks = c("PA injunctive\nnorm 0", "PA injunctive\nnorm 1"),
                      labels = c( 'PA injunctive\nnorm 0' = "Boy", 'PA injunctive\nnorm 1' = "Girl"),
                      values = c("#3bc600", "#0000ff", "#9cc68b", "#8080ff"),
                      name = "", guide = "legend") +
  theme_ridges(grid = FALSE) +
  theme(legend.position="bottom", axis.text=element_text(size=10))

plot2 <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'PA action and\ncoping planning' = PA_actCop_T1,
'PA intention' = PA_intention_T1,
'PA outcome\nexpectations' = PA_oexp_T1,
'PA perceived\nbehavioural control' = PA_pbc_T1,
'PA self efficacy' = PA_selfefficacy_T1,
'PA perceived\nopportunities' = PA_opportunities_T1,
'PA descriptive\nnorm' = PA_dnorm_T1,
'PA injunctive\nnorm' = PA_inorm_T1) %>%
  # select(noquote(order(colnames(.)))) %>% # Orders columns alphabetically
  gather(key = Variable, value = Value, 6:ncol(.), factor_key = TRUE) %>% 
  ggplot(aes(y = Variable)) +
  geom_density_ridges(aes(x = Value, fill = paste(Variable, intervention)), 
           alpha = .6, color = "black", from = 1, to = 7) +
  labs(x = "",
       y = "") +
  scale_y_discrete(expand = c(0.01, 0), labels = NULL) +
  scale_x_continuous(expand = c(0.01, 0)) +
  scale_fill_cyclical(breaks = c("PA injunctive\nnorm 1", "PA injunctive\nnorm 0"),
                      labels = c('PA injunctive\nnorm 1' = "Intervention", 'PA injunctive\nnorm 0' = "Control"),
                      values = c("#ff0000", "#0000ff", "#ff8080", "#8080ff"),
                      name = "", guide = "legend") +
  theme_ridges(grid = FALSE) +
  theme(legend.position="bottom", axis.text=element_text(size=10))

target = c("PA_actCop_T1",
"PA_intention_T1",
"PA_oexp_T1",
"PA_pbc_T1",
"PA_selfefficacy_T1",
"PA_opportunities_T1",
"PA_dnorm_T1",
"PA_inorm_T1")

PA_ci_girls <- ci_girls %>% filter(diamondlabels %in% names(scales_T1) & 
                                     grepl("PA_actCop_T1", diamondlabels) | 
                                     grepl("PA_intention_T1", diamondlabels) | 
                                     grepl("PA_oexp_T1", diamondlabels) | 
                                     grepl("PA_pbc_T1", diamondlabels) | 
                                     grepl("PA_selfefficacy_T1", diamondlabels) | 
                                     grepl("PA_opportunities_T1", diamondlabels) | 
                                     grepl("PA_dnorm_T1", diamondlabels) | 
                                     grepl("PA_inorm_T1", diamondlabels))

PA_ci_girls <- PA_ci_girls[match(target, PA_ci_girls$diamondlabels), ]

PA_ci_boys <- ci_boys %>% filter(diamondlabels %in% names(scales_T1) & 
                                     grepl("PA_actCop_T1", diamondlabels) | 
                                     grepl("PA_intention_T1", diamondlabels) | 
                                     grepl("PA_oexp_T1", diamondlabels) | 
                                     grepl("PA_pbc_T1", diamondlabels) | 
                                     grepl("PA_selfefficacy_T1", diamondlabels) | 
                                     grepl("PA_opportunities_T1", diamondlabels) | 
                                     grepl("PA_dnorm_T1", diamondlabels) | 
                                     grepl("PA_inorm_T1", diamondlabels))

PA_ci_boys <- PA_ci_boys[match(target, PA_ci_boys$diamondlabels), ]

plot1 <- plot1 + 
  diamondPlot(PA_ci_girls, returnLayerOnly = TRUE, color='blue', alpha=.3, fixedSize = 0.15) +
  diamondPlot(PA_ci_boys, returnLayerOnly = TRUE, color='green', alpha=.3, fixedSize = 0.15)

PA_ci_intervention <- ci_intervention %>% filter(diamondlabels %in% names(scales_T1) & 
                                     grepl("PA_actCop_T1", diamondlabels) | 
                                     grepl("PA_intention_T1", diamondlabels) | 
                                     grepl("PA_oexp_T1", diamondlabels) | 
                                     grepl("PA_pbc_T1", diamondlabels) | 
                                     grepl("PA_selfefficacy_T1", diamondlabels) | 
                                     grepl("PA_opportunities_T1", diamondlabels) | 
                                     grepl("PA_dnorm_T1", diamondlabels) | 
                                     grepl("PA_inorm_T1", diamondlabels))

PA_ci_intervention <- PA_ci_intervention[match(target, PA_ci_intervention$diamondlabels), ]

PA_ci_control <- ci_control %>% filter(diamondlabels %in% names(scales_T1) & 
                                     grepl("PA_actCop_T1", diamondlabels) | 
                                     grepl("PA_intention_T1", diamondlabels) | 
                                     grepl("PA_oexp_T1", diamondlabels) | 
                                     grepl("PA_pbc_T1", diamondlabels) | 
                                     grepl("PA_selfefficacy_T1", diamondlabels) | 
                                     grepl("PA_opportunities_T1", diamondlabels) | 
                                     grepl("PA_dnorm_T1", diamondlabels) | 
                                     grepl("PA_inorm_T1", diamondlabels))

PA_ci_control <- PA_ci_control[match(target, PA_ci_control$diamondlabels), ]

plot2 <- plot2 + 
  diamondPlot(PA_ci_intervention, returnLayerOnly = TRUE, color='blue', alpha=.3, fixedSize = 0.15) +
  diamondPlot(PA_ci_control, returnLayerOnly = TRUE, color='red', alpha=.3, fixedSize = 0.15)

# grid.arrange(plot1, plot2, ncol = 2)
grid.newpage()
grid.draw(cbind(ggplotGrob(plot1), ggplotGrob(plot2), size = "first"))
```

## SB determinants

```{r}

plot1 <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'SB intention' = SB_intention_T1,
'SB outcome\nexpectations' = SB_oexp_T1,
'SB self-efficacy\nand perceived\nbehavioural control' = SB_sePbc_T1,
'SB descriptive\nnorm' = SB_dnorm_T1,
'SB injunctive\nnorm' = SB_inorm_T1)  %>%
  # select(noquote(order(colnames(.)))) %>% # Orders columns alphabetically
  gather(key = Variable, value = Value, 6:ncol(.)) %>% 
  ggplot(aes(y = Variable)) +
  geom_density_ridges(aes(x = Value, fill = paste(Variable, girl)), 
           alpha = .6, color = "black", from = 1, to = 7) +
  labs(x = "",
       y = "") +
  scale_y_discrete(expand = c(0.01, 0)) +
  scale_x_continuous(expand = c(0.01, 0)) +
  scale_fill_cyclical(breaks = c("SB injunctive\nnorm 0", "SB injunctive\nnorm 1"),
                      labels = c( 'SB injunctive\nnorm 0' = "Boy", 'SB injunctive\nnorm 1' = "Girl"),
                      values = c("#3bc600", "#0000ff", "#9cc68b", "#8080ff"),
                      name = "", guide = "legend") +
  theme_ridges(grid = FALSE) +
  theme(legend.position="bottom")

plot2 <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
'SB intention' = SB_intention_T1,
'SB outcome\nexpectations' = SB_oexp_T1,
'SB self-efficacy\nand perceived\nbehavioural control' = SB_sePbc_T1,
'SB descriptive\nnorm' = SB_dnorm_T1,
'SB injunctive\nnorm' = SB_inorm_T1) %>%
  # select(noquote(order(colnames(.)))) %>% # Orders columns alphabetically
  gather(key = Variable, value = Value, 6:ncol(.)) %>% 
  ggplot(aes(y = Variable)) +
  geom_density_ridges(aes(x = Value, fill = paste(Variable, intervention)), 
           alpha = .6, color = "black", from = 1, to = 7) +
  labs(x = "",
       y = "") +
  scale_y_discrete(expand = c(0.01, 0), labels = NULL) +
  scale_x_continuous(expand = c(0.01, 0)) +
  scale_fill_cyclical(breaks = c("SB injunctive\nnorm 1", "SB injunctive\nnorm 0"),
                      labels = c('SB injunctive\nnorm 1' = "Intervention", 'SB injunctive\nnorm 0' = "Control"),
                      values = c("#ff0000", "#0000ff", "#ff8080", "#8080ff"),
                      name = "", guide = "legend") +
  theme_ridges(grid = FALSE) +
  theme(legend.position="bottom")

grid.arrange(plot1, plot2, ncol = 2)
```

# CIBER (not included for now)

```{r, eval = FALSE}
p_load(userfriendlyscience)

# cat(names(df), sep = "\",\n\"")

# Make variables numeric, and d as data frame
d_num <- df %>% mutate_all(as.numeric) 
d_num <- as.data.frame(d_num)

CIBER(data = d_num,
      determinants = c(
        "actCop_T1",
        "agrbct_T1",
        "amotivation_T1",
        "autonomous_T1",
        "b5agr_T1.1",
        "b5cons_T1.1",
        "b5ext_T1.1",
        "b5neur_T1.1",
        "b5open_T1.1",
        "controlled_T1",
        "dnorm_T1",
        "frqbct_T1",
        "goal_T1",
        "inorm_T1",
        "intention_T1",
        "oexp_T1",
        "opportunities_T1",
        "pbc_T1",
        "selfefficacy_T1"),
      targets = c("paT1", "fatpct_T1"),
      conf.level = list(means = 0.9999,
                        associations = 0.99)
      )

CIBER(data = d_num,
      determinants = c(
        "actCop_T1",
        "agrbct_T1",
        "frqbct_T1",
        "amotivation_T1",
        "autonomous_T1",
        "controlled_T1",
        "dnorm_T1",
        "intention_T1",
        "oexp_T1",
        "opportunities_T1",
        "sePbc_T1"),
      targets = c("paT1", "fatpct_T1"),
      conf.level = list(means = 0.9999,
                        associations = 0.99)
      )

# to create variable list for CIBER:
# cat(names(d), sep = "\",\n\"")

CIBER(data = d_num,
  determinants = c(
  "agrbct_01_T1",
  "agrbct_02_T1",
  "agrbct_03_T1",
  "agrbct_04_T1",
  "agrbct_05_T1",
  "agrbct_06_T1",
  "agrbct_07_T1",
  "agrbct_08_T1",
  "agrbct_09_T1",
  "agrbct_10_T1",
  "frqbct_01_T1",
  "frqbct_02_T1",
  "frqbct_03_T1",
  "frqbct_04_T1",
  "frqbct_05_T1",
  "frqbct_06_T1",
  "frqbct_07_T1",
  "frqbct_08_T1",
  "frqbct_09_T1"),
   targets = c("MVPA", "SB"),
  leftAnchors = rep("", 19),
  rightAnchors = rep("", 19))

CIBER(data = d_num,
  determinants = c(
  "autonomous_01_T1",
  "autonomous_02_T1",
  "autonomous_03_T1",
  "autonomous_04_T1",
  "autonomous_05_T1",
  "autonomous_06_T1",
  "autonomous_07_T1",
  "autonomous_08_T1",
  "autonomous_09_T1"),
   targets = c("MVPA", "SB"),
  leftAnchors = rep("", 9),
  rightAnchors = rep("", 9))

CIBER(data = d_num,
  determinants = c(
  "intention_01_T1",
  "intention_02_T1",
  "selfefficacy_01_T1",
  "selfefficacy_02_T1",
  "pbc_01_T1",
  "pbc_02_T1",
  "pbc_03_T1",
  "norm_01_T1",
  "norm_02_T1",
  "oexp_01_T1",
  "oexp_02_T1",
  "oexp_03_T1",
  "oexp_04_T1",
  "oexp_05_T1",
  "oexp_06_T1",
  "oexp_07_T1",
  "oexp_08_T1",
  "oexp_09_T1",
  "oexp_10_T1",
  "oexp_11_T1",
  "oexp_12_T1"),
   targets = c("MVPA", "SB"),
  leftAnchors = rep("", 21),
  rightAnchors = rep("", 21))
```

# Density plots

## Accelerometer-measured PA

```{r}

colfill <- c(1,2,3,4,5)

# Create data frame
densplot <- d
levels(densplot$intervention) <- list("Intervention" = "1", "Control" = "0")
levels(densplot$girl) <- list("Girl" = "1", "Boy" = "0")

# This gives side-by-side plots
 layout(matrix(c(1,2,3,3), nrow = 2, ncol = 2, byrow = TRUE), heights=c(2.5, 2))

## Intervention vs. control
# Choose only the variables needed and drop NA
dens <- densplot %>% select(paAccelerometer_T1, intervention) %>% 
  filter(complete.cases(.))

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Make plot
sm.paAccelerometer_T1_1 <- sm.density.compare2(as.numeric(dens$paAccelerometer_T1), as.factor(dens$intervention), xlab="", col=colfill, lty=c(1,2), bandcol='LightGray', model="equal", lwd=(c(2,2)))
legend("topright", levels(dens$intervention), fill=c(1, 2))

## Girls vs. boys
# Choose only the variables needed and drop NA
dens <- densplot %>% select(paAccelerometer_T1, girl) %>% 
  filter(complete.cases(.))

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Make plot
sm.paAccelerometer_T1_2 <- sm.density.compare2(as.numeric(dens$paAccelerometer_T1), as.factor(dens$girl), xlab="", col=colfill, lty=c(1,2), bandcol='LightGray', model="equal", lwd=(c(2,2)))
legend("topright", levels(dens$girl), fill=c(1, 2))

## Differences in schools
# Choose only the variables needed and drop NA
dens <- densplot %>% select(paAccelerometer_T1, school) %>% 
  filter(complete.cases(.))

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Intervention groups with solid thicker lines
linetypes <- c(1,2,2,1,2)

# Make plot
sm.paAccelerometer_T1_3 <- sm.density.compare(as.numeric(dens$paAccelerometer_T1), dens$school, xlab="", col=colfill, lty=linetypes, model="none")
legend("topright", c("Intervention school", "Control school"), col = c(4, 3), lty = c(1, 2), lwd = c(2, 2))

```

## Time spent sitting and lying down

```{r}

colfill <- c(1,2,3,4,5)

# Create data frame
densplot <- d
levels(densplot$intervention) <- list("Intervention" = "1", "Control" = "0")
levels(densplot$girl) <- list("Girl" = "1", "Boy" = "0")

# This gives side-by-side plots
 layout(matrix(c(1,2,3,3), nrow = 2, ncol = 2, byrow = TRUE), heights=c(2.5, 2))

## Intervention vs. control
# Choose only the variables needed and drop NA
dens <- densplot %>% select(sitLieAccelerometer_T1, intervention) %>% 
  filter(complete.cases(.))

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Make plot
sm.sitLieAccelerometer_T1_1 <- sm.density.compare2(as.numeric(dens$sitLieAccelerometer_T1), as.factor(dens$intervention), xlab="", col=colfill, lty=c(1,2), bandcol='LightGray', model="equal", lwd=(c(2,2)))
legend("topright", levels(dens$intervention), fill=c(1, 2))

## Girls vs. boys
# Choose only the variables needed and drop NA
dens <- densplot %>% select(sitLieAccelerometer_T1, girl) %>% 
  filter(complete.cases(.))

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Make plot
sm.sitLieAccelerometer_T1_2 <- sm.density.compare2(as.numeric(dens$sitLieAccelerometer_T1), as.factor(dens$girl), xlab="", col=colfill, lty=c(1,2), bandcol='LightGray', model="equal", lwd=(c(2,2)))
legend("topright", levels(dens$girl), fill=c(1, 2))

## Differences in schools
# Choose only the variables needed and drop NA
dens <- densplot %>% select(sitLieAccelerometer_T1, school) %>% 
  filter(complete.cases(.))

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Intervention groups with solid thicker lines
linetypes <- c(1,2,2,1,2)

# Make plot
sm.sitLieAccelerometer_T1_3 <- sm.density.compare(as.numeric(dens$sitLieAccelerometer_T1), dens$school, xlab="", col=colfill, lty=linetypes, model="none")
legend("topright", c("Intervention school", "Control school"), col = c(4, 3), lty = c(1, 2), lwd = c(2, 2))

```

# Symptoms

```{r}
p_load(grid)

colfill <- c(1,2,3,4,5)

# Create data frame
densplot <- df
levels(densplot$intervention) <- list("Intervention" = "1", "Control" = "0")
levels(densplot$girl) <- list("Girl" = "1", "Boy" = "0")

# This gives side-by-side plots
 layout(matrix(c(1,2,3,3), nrow = 2, ncol = 2, byrow = TRUE), heights=c(2.5, 2))

## Intervention vs. control
# Choose only the variables needed and drop NA
dens <- densplot %>% select(symptom_T1, intervention) %>% na.omit(densplot)

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Make plot
sm.symptom_T1_1 <- sm.density.compare2(as.numeric(dens$symptom_T1), as.factor(dens$intervention), xlab="", col=colfill, lty=c(1,2), bandcol='LightGray', model="equal", lwd=(c(2,2)))
legend("topright", levels(dens$intervention), fill=c(1, 2))

## Girls vs. boys
# Choose only the variables needed and drop NA
dens <- densplot %>% select(symptom_T1, girl)  %>% na.omit(densplot)

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Make plot
sm.symptom_T1_2 <- sm.density.compare2(as.numeric(dens$symptom_T1), as.factor(dens$girl), xlab="", col=colfill, lty=c(1,2), bandcol='LightGray', model="equal", lwd=(c(2,2)))
legend("topright", levels(dens$girl), fill=c(1, 2))

## Differences in schools
# Choose only the variables needed and drop NA
dens <- densplot %>% select("Symptom sum score" = symptom_T1, school) %>% na.omit(densplot)

# Set random number generator for reproducibility of bootstrap test of equal densities
set.seed(10)

# Intervention groups with solid thicker lines
linetypes <- c(1,2,2,1,2)
linewidths <- c(2,1,1,2,1)

# Make plot
sm.symptom_T1_3 <- sm.density.compare(dens$`Symptom sum score`, dens$school, xlab="", col=colfill, lty=linetypes, model="equal", lwd=linewidths)
xlab = ""


```

## Symptom histograms

### intervention / gender

```{r}

sympGirls <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
  "Neck and shoulder pain" = symptom_neckShoulderPain_T1,
  "Lower back pain" = symptom_lowerBackPain_T1,
  "Stomach ache" = symptom_stomachAche_T1,
  "Tension or nervousness" = symptom_tensionNervousness_T1,
  "Irritability or anger bursts" = symptom_irritabilityAngerbursts_T1,
  "Difficulty with sleep" = symptom_sleepDifficulty_T1,
  "Headache" = symptom_headAche_T1,
  "Tiredness or faintness" = symptom_tirednessFaintness_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(girl == "1") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:4), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("darkolivegreen2", "darkolivegreen4")) +
  labs(title = "Girls") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5, size = 10),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 4.5))

sympBoys <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
  "Neck and shoulder pain" = symptom_neckShoulderPain_T1,
  "Lower back pain" = symptom_lowerBackPain_T1,
  "Stomach ache" = symptom_stomachAche_T1,
  "Tension or nervousness" = symptom_tensionNervousness_T1,
  "Irritability or anger bursts" = symptom_irritabilityAngerbursts_T1,
  "Difficulty with sleep" = symptom_sleepDifficulty_T1,
  "Headache" = symptom_headAche_T1,
  "Tiredness or faintness" = symptom_tirednessFaintness_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(girl == "0") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:4), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("darkolivegreen2", "darkolivegreen4")) +
  labs(title = "Boys") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5, size = 10),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 4.5))

sympInt <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
  "Neck and shoulder pain" = symptom_neckShoulderPain_T1,
  "Lower back pain" = symptom_lowerBackPain_T1,
  "Stomach ache" = symptom_stomachAche_T1,
  "Tension or nervousness" = symptom_tensionNervousness_T1,
  "Irritability or anger bursts" = symptom_irritabilityAngerbursts_T1,
  "Difficulty with sleep" = symptom_sleepDifficulty_T1,
  "Headache" = symptom_headAche_T1,
  "Tiredness or faintness" = symptom_tirednessFaintness_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(intervention == "1") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:4), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "") +
  scale_fill_cyclical(values = c("deepskyblue", "deepskyblue4")) +
  labs(title = "Intervention") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5, size = 10),
        axis.text=element_text(size=10)) +
coord_cartesian(xlim = c(0.5, 4.5))

sympCont <- df %>% dplyr::select(id,
  intervention,
  group,
  school,
  girl,
  "Neck and shoulder pain" = symptom_neckShoulderPain_T1,
  "Lower back pain" = symptom_lowerBackPain_T1,
  "Stomach ache" = symptom_stomachAche_T1,
  "Tension or nervousness" = symptom_tensionNervousness_T1,
  "Irritability or anger bursts" = symptom_irritabilityAngerbursts_T1,
  "Difficulty with sleep" = symptom_sleepDifficulty_T1,
  "Headache" = symptom_headAche_T1,
  "Tiredness or faintness" = symptom_tirednessFaintness_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(intervention == "0") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:4), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("deepskyblue", "deepskyblue4")) +
  labs(title = "Control") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5, size = 10),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 4.5))

#grid.arrange(sympInt, sympGirls, sympCont, sympBoys, ncol = 2)

# ("Seldom or never", "About once a month", "About once a week", "Almost daily")

# This draws all histograms next to each other:
grid.newpage()
grid.draw(cbind(ggplotGrob(sympInt), ggplotGrob(sympCont), ggplotGrob(sympGirls), ggplotGrob(sympBoys), size = "last"))

# This draws 2 histograms per row:
#grid.newpage()
#grid.draw(rbind(cbind(ggplotGrob(sympInt), ggplotGrob(sympCont), size = "last"), cbind(ggplotGrob(sympGirls), ggplotGrob(sympBoys), size = "last")))


```

### educational track

```{r}

sympHRC <- df %>% dplyr::select(id,
  intervention,
  track,
  school,
  girl,
  "Neck and shoulder pain" = symptom_neckShoulderPain_T1,
  "Lower back pain" = symptom_lowerBackPain_T1,
  "Stomach ache" = symptom_stomachAche_T1,
  "Tension or nervousness" = symptom_tensionNervousness_T1,
  "Irritability or anger bursts" = symptom_irritabilityAngerbursts_T1,
  "Difficulty with sleep" = symptom_sleepDifficulty_T1,
  "Headache" = symptom_headAche_T1,
  "Tiredness or faintness" = symptom_tirednessFaintness_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(track == "HRC") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:4), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("darkolivegreen2", "darkolivegreen4")) +
  labs(title = "HRC") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5, size = 10),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 4.5))

sympNursing <- df %>% dplyr::select(id,
  intervention,
  track,
  school,
  girl,
  "Neck and shoulder pain" = symptom_neckShoulderPain_T1,
  "Lower back pain" = symptom_lowerBackPain_T1,
  "Stomach ache" = symptom_stomachAche_T1,
  "Tension or nervousness" = symptom_tensionNervousness_T1,
  "Irritability or anger bursts" = symptom_irritabilityAngerbursts_T1,
  "Difficulty with sleep" = symptom_sleepDifficulty_T1,
  "Headache" = symptom_headAche_T1,
  "Tiredness or faintness" = symptom_tirednessFaintness_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(track == "Nursing") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:4), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("darkolivegreen2", "darkolivegreen4")) +
  labs(title = "Nursing") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5, size = 10),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 4.5))

sympIT <- df %>% dplyr::select(id,
  intervention,
  track,
  school,
  girl,
  "Neck and shoulder pain" = symptom_neckShoulderPain_T1,
  "Lower back pain" = symptom_lowerBackPain_T1,
  "Stomach ache" = symptom_stomachAche_T1,
  "Tension or nervousness" = symptom_tensionNervousness_T1,
  "Irritability or anger bursts" = symptom_irritabilityAngerbursts_T1,
  "Difficulty with sleep" = symptom_sleepDifficulty_T1,
  "Headache" = symptom_headAche_T1,
  "Tiredness or faintness" = symptom_tirednessFaintness_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(track == "Business IT") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:4), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "") +
  scale_fill_cyclical(values = c("deepskyblue", "deepskyblue4")) +
  labs(title = "Business IT") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5, size = 10),
        axis.text=element_text(size=10)) +
coord_cartesian(xlim = c(0.5, 4.5))

sympBA <- df %>% dplyr::select(id,
  intervention,
  track,
  school,
  girl,
  "Neck and shoulder pain" = symptom_neckShoulderPain_T1,
  "Lower back pain" = symptom_lowerBackPain_T1,
  "Stomach ache" = symptom_stomachAche_T1,
  "Tension or nervousness" = symptom_tensionNervousness_T1,
  "Irritability or anger bursts" = symptom_irritabilityAngerbursts_T1,
  "Difficulty with sleep" = symptom_sleepDifficulty_T1,
  "Headache" = symptom_headAche_T1,
  "Tiredness or faintness" = symptom_tirednessFaintness_T1) %>%
 gather(key = Variable, value = Value, 6:ncol(.)) %>%
  filter(track == "Business Admin") %>% 
 ggplot(aes(x = Value, y = Variable, group = Variable)) +
  geom_density_ridges2(aes(fill = Variable), stat = "binline", binwidth = 1, scale = 0.95) +
  scale_x_continuous(breaks = c(1:4), expand = c(0, 0),
                     name = "") +
  scale_y_discrete(expand = c(0.01, 0), name = "", labels = NULL) +
  scale_fill_cyclical(values = c("deepskyblue", "deepskyblue4")) +
  labs(title = "Business Admin") +
  guides(y = "none") +
  theme_ridges(grid = FALSE) +
  theme(axis.title.x = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5, size = 10),
        axis.text=element_text(size=10, face="bold")) +
coord_cartesian(xlim = c(0.5, 4.5))

#grid.arrange(sympIT, sympHRC, sympBA, sympNursing, ncol = 2)

# ("Seldom or never", "About once a month", "About once a week", "Almost daily")

# This draws all histograms next to each other:
grid.newpage()
grid.draw(cbind(ggplotGrob(sympIT), ggplotGrob(sympBA), ggplotGrob(sympHRC), ggplotGrob(sympNursing), size = "last"))

# This draws 2 histograms per row:
#grid.newpage()
#grid.draw(rbind(cbind(ggplotGrob(sympIT), ggplotGrob(sympBA), size = "last"), cbind(ggplotGrob(sympHRC), ggplotGrob(sympNursing), size = "last")))


```



sm:n testi:
library(sm)
dftest <- data.frame(value = sample(seq(from = 1, to = 7, by = 0.2), size = 1000, replace = TRUE),
                     group = sample(1:5, size = 1000, replace = TRUE))
sm.symptom_T1_3 <- sm.density.compare(dftest$value, dftest$group, xlab="", col=colfill, lty=linetypes, model="equal", lwd=linewidths)
